### 2014-04-09 Manuscript/Phase_detectors_notes.tex
First commit - latex notes

\documentclass{article}
\title{Phase paper}
\author{}
\date{}
\begin{document}
\maketitle

\section{Questions}

\begin{itemize}
\item How do you detect phase
\begin{itemize}
\item What are the methods of phase detection
\end{itemize}
\item What can you do with phase once you have it
\item What does phase tell you with respect to physiological systems
\end{itemize}

\section{Problems}

\begin{itemize}
\item noise in data
\item phase slips
\item time-varying frequencies in data
\item choosing how to access the frequencies of interest
\begin{itemize}
\item bandpass and use a range of frequencies
\item methods of choosing the correct frequency at which to acquire the phase
\end{itemize}
\end{itemize}

\section{Methods}
\begin{itemize}
\item Filters
\begin{itemize}
\item filter types and their effects on data
\end{itemize}
\item Phase detectors
\begin{itemize}
\item Hilbert transform
\begin{itemize}
\item what does the HT actually do
\end{itemize}
\item Wavelets
\item Fourier transform
\begin{itemize}
\item is this different from HT and how
\end{itemize}
\end{itemize}
\item Choosing frequency for phase detection
\begin{itemize}
\item averaging frequencies (Hilbert)
\item maximum likelihood method
\item line fitting
\end{itemize}
\end{itemize}

\section{Data}
\begin{itemize}
\item Human
\begin{itemize}
\item BP
\item IBI
\item CBF
\item SCG
\end{itemize}
\item Rat
\begin{itemize}
\item BP
\item RBF
\item Speckle contrast
\end{itemize}
\item Simulation
\begin{itemize}
\item Time series with multiple frequencies corresponding to the systems we are investigating
\begin{itemize}
\item{heart rate}
\item{interbeat interval}
\item{meyer waves?}
\item{myogenic mechanism in kidney}
\item{tubuloglomerular feedback}
\item{respiration?}
\item{others?}
\end{itemize}
\item{set frequencies and adjust them}
\item{add noise to the signal at varying levels}
\item{Make an interaction between two oscillators}
\begin{itemize}
\item{seems like differential equation}
\end{itemize}
\end{itemize}
\end{itemize}
\end{document}

### 2014-04-10 Matlab/Time_varying_sinewave.m
makes a sine wave with time varying frequency

@@ -1,0 +1,24 @@
+  %% time varying signal
+  
+  % options
+n = 10; % # frequencies 
+fmean = 0.1; % Hz 
+nsamples = 1e3; % # samples per constant freq period
+% freq
+tdur=1/fmean; 
+ts = tdur/nsamples; 
+f = (fmean/2)*randn(n,1)/3 + fmean;
+fvec = []; 
+for i=1:n, fvec = [fvec , f(i)*ones(1,nsamples)]; 
+end
+% algo
+fac_old = 0; 
+for i=1:length(fvec), fac = fac_old + fvec(i)*ts; 
+    y(i) = sin(2*pi*fac); 
+    fac_old = fac; 
+end
+% plot
+subplot(211) 
+    plot(0:tdur:tdur*(n-1),f,'k.',[0 tdur*n],fmean/2*[1 1],[0 tdur*n],fmean*[1.5 1.5]), ylim([0.25 1.75]*fmean)
+subplot(212)
+    plot(0:ts:ts*(length(y)-1),y)

### 2014-04-12 Matlab/MkFreqSpectrum.m
Added 3 Matlab files. Only MkSgateData2 actually works. I can't make heads or tails of the phase it returns, though. You can run it using the parameters in ExParams.

@@ -1,0 +1,40 @@
+function [ FreqSpectrum, PhaseInfo ] = MkFreqSpectrum(Length, dt,...
+    PeakX1, PeakY1, STD1, Phase1, PeakX2, PeakY2, STD2, Phase2)
+%[ FreqSpectrum ] = MkFreqSpectrum(Length, dt, Peak1, STD1, Phase1, Peak2, STD2, Phase2)
+%
+%MkFreqSpectrum creates a frequency spectrum with 2 peaks using an addition
+%of 2 gaussians of height PeakY, frequency PeakX, and standard deviation
+%STD.
+%
+%Inputs
+%   Length: the length in seconds, of the required data
+%   dt: the data aquisition rate, in seconds
+%   PeakX1: the frequency of the first oscillator
+%   PeakY1: the power of the first oscillator in units*seconds
+%   STD1: the standard deviation of the Gaussian creating Peak1
+%   Phase1: Phase (in radians) of the first peak
+%   PeakX2, PeakY2, STD2, Phase2: same as for 1
+%   
+%Outputs
+%   FreqSpectrum: the real part of the Fourier transform.
+%   PhaseInfo: the imaginary part of the Fourier transform. It returns
+%   Phase1 when the first Gaussian is bigger than the second, and vice
+%   versa.
+%%
+%Notes:
+%
+%%
+Freqs = (1:2*Length/dt)./Length;
+Gaussian1 = PeakY1.*gaussmf(Freqs,[STD1 PeakX1]);
+Gaussian1 = Gaussian1.*([ones(length(Freqs(Freqs<PeakX1))),1,-ones(length(Freqs(Freqs>PeakX1)))]);
+Gaussian2 = PeakY2.*gaussmf(Freqs,[STD2 PeakX2]);
+Gaussian1 = Gaussian2.*([ones(length(Freqs(Freqs<PeakX2))),1,-ones(length(Freqs(Freqs>PeakX2)))]);
+FreqSpectrum = Gaussian1+Gaussian2;
+FreqSpectrum = [0, FreqSpectrum];
+%%
+TotalPhase = Phase2*ones(size(Gaussian1));
+TotalPhase( abs(Gaussian1)>abs(Gaussian2) ) = Phase1;
+TotalPhase( abs(Gaussian1)<abs(Gaussian2) ) = Phase2;
+TotalPhase = [0, TotalPhase];
+PhaseInfo = tan(TotalPhase).*FreqSpectrum;
+end

### 2014-04-12 Matlab/MkSgateData.m

@@ -1,0 +1,31 @@
+function [ SgateData ] = MkSgateData(Length, dt,...
+    PeakX1, PeakY1, STD1, Phase1, PeakX2, PeakY2, STD2, Phase2)
+%[ SgateData ] = MkSgateData(Length, dt, Peak1, Phase1, Peak2, Phase2)
+%
+%MkSgateData creates a time series of (Length) seconds with 2 peaks in its frequency spectrum.
+%
+%Inputs
+%   Length: the length in seconds, of the required data
+%   dt: the data aquisition rate, in seconds
+%   PeakX1: the frequency of the first oscillator
+%   PeakY1: the power of the first oscillator in units*seconds
+%   STD1: the width factor of the Gaussian creating Peak1
+%   Phase1: Phase (in radians) of the first peak
+%   PeakX2, PeakY2, STD2, Phase2: same as for 1
+%
+%Outputs
+%   SgateData: The time series
+%%
+%Notes: 
+%Maybe add some noise to the phase.
+%This phase does NOT model time delay. it assumes a driving 'oscillator'
+%that has a certain phase.
+%%
+[ FreqSpectrum, PhaseInfo ] = MkFreqSpectrum(Length, dt,...
+    PeakX1, PeakY1, STD1, Phase1, PeakX2, PeakY2, STD2, Phase2);
+DataFDomain = FreqSpectrum + 1i.*PhaseInfo;
+SgateData = ifft(DataFDomain);
+SgateData = real(SgateData);
+SgateData = SgateData(1:round(length(SgateData)/2));
+end
+

### 2014-04-12 Matlab/MkSgateData2.m

@@ -1,0 +1,38 @@
+function [ SgateData ] = MkSgateData2( Length, dt,...
+    Freq1, Power1, STD1, Phase1, Freq2, Power2, STD2, Phase2)
+%[ SgateData ] = MkSgateData2( Length, dt, Freq1, Power1, STD1, Phase1, Freq2, Power2, STD2, Phase2)
+%
+%SgateData creates a time series from 2 oscillators of frequencies Freq1
+%and Freq2, Phase1 and Phase2, with some frequency noise related to STD1 and STD2
+%
+%Length: length of the time series in seconds
+%dt: sampling rate in seconds
+%%
+Time = (dt:dt:Length);
+Order = 100;
+%%
+Oscillator1= zeros(size(Time));
+Fuzz = STD1*randn(Order,1);
+for N=1:Order
+    FuzzyFreq = Freq1+Fuzz(N);
+    FuzzyPhase = Phase1 +Fuzz(N);
+    FuzzyPower = Power1*(max(abs(Fuzz))-abs(Fuzz(N)))/...
+        sum(max(abs(Fuzz))-abs(Fuzz));
+    Oscillator1=Oscillator1+ FuzzyPower*...
+        sin((Time)*(2*pi)*(FuzzyFreq)-FuzzyPhase);
+end
+%%
+Oscillator2= zeros(size(Time));
+Fuzz = STD2*randn(Order,1);
+for N=1:Order
+    FuzzyFreq = Freq2 + Fuzz(N);
+    FuzzyPhase = Phase2 + Fuzz(N);
+    FuzzyPower = Power2*(max(abs(Fuzz))-abs(Fuzz(N)))/...
+        sum(max(abs(Fuzz))-abs(Fuzz));
+    Oscillator2=Oscillator2+ FuzzyPower*...
+        sin((Time)*(2*pi)*(FuzzyFreq)-FuzzyPhase);
+end
+%%
+SgateData = Oscillator1+Oscillator2;
+end
+

### 2014-05-13 Manuscript/Phase_detectors_outline.tex
outline

\documentclass{article}
\title{Phase paper outline}
\author{}
\date{}
\begin{document}
\maketitle

\section*{Destination journal}
We would like to submit to an engineering journal. The reason is that we are not developing a \textit{seminal} work, just applying existing methods to multiple new applications. The journal will probably be a non-glamourous IEEE, a general physiology journal, or physiological methods journal.

\section*{Purpose of extracting phase information}

\subsection*{Instantaneous phase}
We are looking for the interaction between two oscillating physiological systems. Either we are looking for the relationship between two mutually synchronized oscillators, \textit{e.g.} renal autoregulation synchronization, or forced unidirectional synchronization \textit{e.g.} postural control indices and blood pressure.

The way these interactions are detected is by phase difference, or by phase relationships over time.

In order to get phase relationships, we need to extract instantaneous phase. There are multiple methods for determining instantaneous phase, but it is not clear which one is best, or even if there is a general "best" method.
\begin{enumerate}
\item Hilbert transform
\item Wavelet transform
\item Short time Fourier transform
\item Peak detection
\end{enumerate}

We will use these methods to determine when to use each particular method, and whether or not each should be used at all.

\subsection*{Time-averaged phase}

We should investigate the purposes of average phase. This is most likely to find signatures of regulation between one variable and another, or to find time delays. Regulation of one variable and another can result in a positive phase while time delays can cause negative phase.

\end{document}

### 2014-05-13 Manuscript/Phase_detectors_outline.tex
Added to outline

@@
 This is most likely to find signatures of regulation between one variable and another, or to find time delays.
-Regulation of one variable and another can result in a positive phase while time delays can cause negative phase.
+Regulation of one variable by another can result in a positive phase while time delays can cause negative phase.
+
+\section*{Introduction}
+\begin{itemize}
+\item Physiological regulatory systems are reliably non-linear in their responses
+\item Signal transduction, be it physical signals like pressure or cellular signals like phosphorylation, introduces a delay between input and output. 
+\item Non-linearities and delays conspire to generate oscillations in physiological control systems, for example oscillations in renal blood flow, or oscillations in cerebral blood flow.
+\item Oscillating physiological systems can become synchronized if they are somehow physically coupled. For example, sinus arrhythmia caused by respiration. 
+\item Phase information extracted from each oscillating system can provide information about the relationship between the two systems.
+\item Phase is essentially how far along a cycle a particular oscillation is. 
+\item The problem is that phase has been extracted by multiple different methods, and it is unclear whether there is a best option, or if specific methods are ideal for specific purposes.
+\item Noise and time-variance present in physiological data makes this process more difficult.
+\item The goal of this paper is to identify the most accurate methods of extracting phase information and determine how to deal with common hurdles present in physiological data.
+\end{itemize}
+
+\section*{Methods}
+
+\subsection*{Phase detectors}
+\begin{itemize}
+\item Peak detection
+\item Autoregressive modelling
+\item Short time Fourier transform
+\item Hilbert transform
+\item Wavelet transform
+\end{itemize}
+
+\subsection*{Simulation}
+\begin{itemize}
+\item Generation of data
+	\begin{itemize}
+	\item A sinusoidal signal containing (number?) frequencies were generated to resemble a typical arterial pressure recording. 
+	\item A second sinusoidal signal was generated so that it was the same as the original signal except each frequency was time-varying within a narrow range.
+	\item Noise was added to the signal at increasing levels so SNR ranged from $1-100 dB$
+	\item Each frequency was isolated with a bandpass filter (elliptic?)
+	\end{itemize}
+\item Testing the phase detectors
+	\begin{itemize}
+	\item Each phase detector was used to determine the instantaneous phase of each frequency band isolated from the simulated data
+	\end{itemize}
+
+\subsection*{Physiological data}
+\begin{itemize}
+\item 
+\end{itemize}
+
+\end{itemize}
 

### 2014-05-15 Matlab/Generate_TV_signal.m
create time-varying sine and show TFR

@@ -1,0 +1,36 @@
+%%% generate TV signal %%%
+
+f1 = 0.04; %low frequency
+f2 = 0.1; % high frequency
+len = 500; % duration in seconds
+AM = 1; % amplitude modulation 
+FM = 1; % frequency modulation
+noi = 1; % add GWN
+t = 1:len;
+
+[x]=test_sig_AMFM(f1,f2,len,AM,FM,noi);
+
+
+ 
+res=256; %frequency resolution
+dt=1; %sampling rate
+dj=0.0625; %wavelet interval
+J1=127; %total # of scales
+pad=1; %zero-pad signals
+s0=2*dt; %set initial scale
+mother='Morlet'; %wavelet shape
+param=6; %initial wavelet order
+az = 63;
+el = 46;
+
+%computes the wavelets
+[WN1,~,scales] = wavelet(x,dt,pad,dj,s0,J1,mother,param);
+freq=1./(1.033*scales);
+power = abs(WN1).^2;
+
+mesh(t,freq,power)
+view(az,el)
+xlabel('Time (s)')
+ylabel('Frequency (Hz)')
+zlabel('Power (Units^2/Hz)')
+

### 2014-05-15 Matlab/hilbert_interp.m
estimate phase with Hilbert

@@ -1,0 +1,27 @@
+function [phh,phhu,phhw,w,wi] =  hilbert_interp(x)
+
+
+xh = hilbert(x);
+phh = angle(xh);
+phhu = unwrap(phh);
+
+    w = diff(phhu).*(2*2/pi);
+    wi = w;
+%%
+t = 1:length(x);
+k1=find(wi<0);
+kk1=[k1;k1+1;k1-1];
+kk1(kk1<=0)=[];
+kk1(kk1>length(wi))=[];
+ti=t(2:end);
+tt=ti;
+tt(kk1)=[];
+wi(kk1)=[];
+wi=interp1(tt,wi,ti,'linear','extrap');
+%%
+phh4=phh(2:end);
+phh4(kk1)=[];
+phh4=interp1(tt,phh4,ti,'linear','extrap')';
+
+phhw = wrapToPi(phh4);
+end

### 2014-05-15 Manuscript/Phase_detectors_outline.tex
started methods

@@
 The journal will probably be a non-glamourous IEEE, a general physiology journal, or physiological methods journal.
+
+\subsection*{Potential physiology journals}
+
+\begin{itemize}
+\item Acta physiologica
+\item Physiological Reports
+\item AJP Heart/regulatory - Innovative methodology
+\item The Journal of Physiology - techniques for physiology \textit{I think this kind of thing might be best}
+\item The Journal of General Physiology - methods and approaches
+\item Physiological measurement
+\item Journal of experimental physiology
+\end{itemize}
+
+\subsection*{Potential engineering journals}
+\begin{itemize}
+\item IEEE transactions on biomedical engineering
+\item IEEE transactions on signal processing
+\item IEEE signal processing letters
+\item Signal processing and control
+\item Signal processing
+\item Annals of biomedical engineering
+\end{itemize}
 
@@
 	\item Each phase detector was used to determine the instantaneous phase of each frequency band isolated from the simulated data
+	\item The accuracy of the estimated instantaneous phase was calculated as ???
 	\end{itemize}
+
+\subsection*{Accuracy of phase estimates}
+Accuracy $A$ is the mean difference between the estimated phase of a signal and its true phase. 
+$$ A = \frac{1}{N} \sum_{m=1}^{N} \frac{\left| \phi _{true} (t) - \phi _{est} (t) \right|}{\phi _{true} (t)} $$
 
@@
 \begin{itemize}
-\item 
+\item Renal cortical perfusion
+	\begin{itemize}
+	\item phase synchronization among regions of the kidney
+	\end{itemize}
+\item BP and Heart rate
+	\begin{itemize}
+	\item phase lag between changes in heart rate and changes in BP
+	\end{itemize}
+\item Something about SCG or ECG
+\item cerebral blood flow
 \end{itemize}

### 2014-05-20 Matlab/InstaPhaseWavelet.m
I fixed MkSgateData2.m. There is an issue with frequency where the specified frequencies HAVE to be part of the basis that you use in the fft.

@@ -1,0 +1,8 @@
+function [ InstaPhase ] = InstaPhaseWavelet( Signal1, dt )
+%[ InstaPhase ] = InstaPhaseWavelet( Signal1 )
+%%
+Time = (0:dt:length(Signal1)-1);
+[Wave,Period,~,~] = wavelet(Signal1,dt,0, 0.25, 100, 25);
+figure(3); clf; imagesc(Time,Period,2.*abs(Wave));
+end
+

### 2014-05-20 Matlab/MkSgateData2.m

@@ -1,4 +1,4 @@
-function [ SgateData ] = MkSgateData2( Length, dt,...
+function [ SgateData, Time, Freqs ] = MkSgateData2( Length, dt,...
     Freq1, Power1, STD1, Phase1, Freq2, Power2, STD2, Phase2)
 %[ SgateData ] = MkSgateData2( Length, dt, Freq1, Power1, STD1, Phase1, Freq2, Power2, STD2, Phase2)
 %
@@ -8,18 +8,26 @@ function [ SgateData ] = MkSgateData2( Length, dt,...
 %Length: length of the time series in seconds
 %dt: sampling rate in seconds
 %%
-Time = (dt:dt:Length);
-Order = 100;
+Time = (0:dt:Length);
+Freqs = (Time(1:ceil(length(Time)/2))./(length(Time)))./dt^2;
+Order = 1000;
 %%
 Oscillator1= zeros(size(Time));
 Fuzz = STD1*randn(Order,1);
+Fuzz2 = STD1*randn(Order,1)/5;
+Fuzz=Fuzz-mean(Fuzz);
+Fuzz2=fliplr(Fuzz2)-mean(fliplr(Fuzz2));
 for N=1:Order
-    FuzzyFreq = Freq1+Fuzz(N);
-    FuzzyPhase = Phase1 +Fuzz(N);
+    N
+    [~, Mindex] = min(abs(Freqs-(Freq1+Fuzz(N))));
+    FuzzyFreq = Freqs(Mindex);
+%    FuzzyFreq = (Freq1+Fuzz(N));
+    FuzzyPhase = Phase1+Fuzz2(N);
     FuzzyPower = Power1*(max(abs(Fuzz))-abs(Fuzz(N)))/...
         sum(max(abs(Fuzz))-abs(Fuzz));
-    Oscillator1=Oscillator1+ FuzzyPower*...
-        sin((Time)*(2*pi)*(FuzzyFreq)-FuzzyPhase);
+%   FuzzyPower=1;
+    Oscillator1=Oscillator1+ awgn(FuzzyPower*...
+        cos((Time)*(2*pi)*(FuzzyFreq)-FuzzyPhase),4,'measured');
 end
 %%
 Oscillator2= zeros(size(Time));
@@ -30,9 +38,10 @@ for N=1:Order
     FuzzyPower = Power2*(max(abs(Fuzz))-abs(Fuzz(N)))/...
[…]

### 2014-05-20 Matlab/Time_varying_sinewave.m

@@ -17,8 +17,9 @@ for i=1:length(fvec), fac = fac_old + fvec(i)*ts;
     y(i) = sin(2*pi*fac); 
     fac_old = fac; 
 end
+Time = 0:ts:ts*(length(y)-1);
 % plot
 subplot(211) 
     plot(0:tdur:tdur*(n-1),f,'k.',[0 tdur*n],fmean/2*[1 1],[0 tdur*n],fmean*[1.5 1.5]), ylim([0.25 1.75]*fmean)
 subplot(212)
-    plot(0:ts:ts*(length(y)-1),y)
+    plot(Time,y)

### 2014-05-20 Matlab/InstaPhaseWavelet.m
deleted some old useless matlab files

@@ -1,8 +1,0 @@
-function [ InstaPhase ] = InstaPhaseWavelet( Signal1, dt )
-%[ InstaPhase ] = InstaPhaseWavelet( Signal1 )
-%%
-Time = (0:dt:length(Signal1)-1);
-[Wave,Period,~,~] = wavelet(Signal1,dt,0, 0.25, 100, 25);
-figure(3); clf; imagesc(Time,Period,2.*abs(Wave));
-end
-

### 2014-05-20 Matlab/MkFreqSpectrum.m

@@ -1,40 +1,0 @@
-function [ FreqSpectrum, PhaseInfo ] = MkFreqSpectrum(Length, dt,...
-    PeakX1, PeakY1, STD1, Phase1, PeakX2, PeakY2, STD2, Phase2)
-%[ FreqSpectrum ] = MkFreqSpectrum(Length, dt, Peak1, STD1, Phase1, Peak2, STD2, Phase2)
-%
-%MkFreqSpectrum creates a frequency spectrum with 2 peaks using an addition
-%of 2 gaussians of height PeakY, frequency PeakX, and standard deviation
-%STD.
-%
-%Inputs
-%   Length: the length in seconds, of the required data
-%   dt: the data aquisition rate, in seconds
-%   PeakX1: the frequency of the first oscillator
-%   PeakY1: the power of the first oscillator in units*seconds
-%   STD1: the standard deviation of the Gaussian creating Peak1
-%   Phase1: Phase (in radians) of the first peak
-%   PeakX2, PeakY2, STD2, Phase2: same as for 1
-%   
-%Outputs
-%   FreqSpectrum: the real part of the Fourier transform.
-%   PhaseInfo: the imaginary part of the Fourier transform. It returns
-%   Phase1 when the first Gaussian is bigger than the second, and vice
-%   versa.
-%%
-%Notes:
-%
-%%
-Freqs = (1:2*Length/dt)./Length;
-Gaussian1 = PeakY1.*gaussmf(Freqs,[STD1 PeakX1]);
-Gaussian1 = Gaussian1.*([ones(length(Freqs(Freqs<PeakX1))),1,-ones(length(Freqs(Freqs>PeakX1)))]);
-Gaussian2 = PeakY2.*gaussmf(Freqs,[STD2 PeakX2]);
-Gaussian1 = Gaussian2.*([ones(length(Freqs(Freqs<PeakX2))),1,-ones(length(Freqs(Freqs>PeakX2)))]);
-FreqSpectrum = Gaussian1+Gaussian2;
-FreqSpectrum = [0, FreqSpectrum];
-%%
-TotalPhase = Phase2*ones(size(Gaussian1));
-TotalPhase( abs(Gaussian1)>abs(Gaussian2) ) = Phase1;
-TotalPhase( abs(Gaussian1)<abs(Gaussian2) ) = Phase2;
-TotalPhase = [0, TotalPhase];
-PhaseInfo = tan(TotalPhase).*FreqSpectrum;
-end

### 2014-05-20 Matlab/MkSgateData.m

@@ -1,31 +1,0 @@
-function [ SgateData ] = MkSgateData(Length, dt,...
-    PeakX1, PeakY1, STD1, Phase1, PeakX2, PeakY2, STD2, Phase2)
-%[ SgateData ] = MkSgateData(Length, dt, Peak1, Phase1, Peak2, Phase2)
-%
-%MkSgateData creates a time series of (Length) seconds with 2 peaks in its frequency spectrum.
-%
-%Inputs
-%   Length: the length in seconds, of the required data
-%   dt: the data aquisition rate, in seconds
-%   PeakX1: the frequency of the first oscillator
-%   PeakY1: the power of the first oscillator in units*seconds
-%   STD1: the width factor of the Gaussian creating Peak1
-%   Phase1: Phase (in radians) of the first peak
-%   PeakX2, PeakY2, STD2, Phase2: same as for 1
-%
-%Outputs
-%   SgateData: The time series
-%%
-%Notes: 
-%Maybe add some noise to the phase.
-%This phase does NOT model time delay. it assumes a driving 'oscillator'
-%that has a certain phase.
-%%
-[ FreqSpectrum, PhaseInfo ] = MkFreqSpectrum(Length, dt,...
-    PeakX1, PeakY1, STD1, Phase1, PeakX2, PeakY2, STD2, Phase2);
-DataFDomain = FreqSpectrum + 1i.*PhaseInfo;
-SgateData = ifft(DataFDomain);
-SgateData = real(SgateData);
-SgateData = SgateData(1:round(length(SgateData)/2));
-end
-

### 2014-05-21 Manuscript/Phase_detectors_bkgrnd_methods.tex
big commit - sorry

\documentclass{article}
\author{}
\date{}
\title{Phase detectors}
\begin{document}
\maketitle

\section{Introduction}

We are considering oscillators. Examples are the oscillatory blood pressure caused by heart rate, or oscillating cerebral or renal blood flow caused by myogenic activity. An oscillation has multiple properties that describe its behaviour. Frequency is the number of complete oscillations per unit time. Phase is the position of an oscillation along its cycle. The start of an oscillation has zero phase and the end of one cycle has $2\pi$ radians phase. Phase is a continuous variable that is constantly increasing as an oscillation progresses. We wrap phase to the interval $[-\pi,\pi]$ or $[0,2\pi]$ for interpretation purposes, but the increasing property of phase can be useful. The faster an oscillation, the faster the phase will increase, such that the rate of increase in phase is equal to the frequency (1). 
$$ f(t) = \frac{1}{2\pi} \cdot \varphi\left(t\right)'$$
Therefore detection of phase can be performed using specific phase detectors or by finding instantaneous frequency and then taking the integral.

\section{Hilbert transform}
The HT is the transformation of a real valued signal $x(t)$ into a complex signal $\hat{x}(t)$ (2) which is the same as $x(t)$ except it has an imaginary component that contains instantaneous phase information.

$$ z(t)=\cos (2\pi f_1 t) e^{(j 2\pi f_2 t)}$$

The inventor of this technique (Gabor 1946) called $\hat{x}(t)$ the analytic signal. The arc tangent of this signal is the instantaneous phase $\varphi (t)$.

\section{Wavelet transform}
Wavelets are small waves that can be used to identify transient frequencies. Generally, a wavelet function (3) is convolved with a time series as the wavelet is dilated in scale and shifted in time. The function for $\psi$ is called the mother function, and defines the shape of the wavelet. The most commonly used is the Morlet mother function (4), where $\omega_0$ is the center frequency of the wavelet.

$$ W(t,s) = \frac{1}{\sqrt{s}} \int_{-\infty}^\infty x(\tau)\psi ^\star (\frac{\tau -t}{s}) d\tau $$
$$ \psi (t) = \pi^{-\frac{1}{4}}e^{i \omega_0 t}e^{\frac{-t^2}{2}} $$

\section{Wigner-Ville distribution}
The Wigner-Ville distribution is a maethod of time frequency representation of a signal that provides further accuracy.
\end{document}

### 2014-05-21 Matlab/time_var_signal.m

@@ -1,0 +1,30 @@
+function [y,f] = time_var_signal(nfreqs,fmean,fs,plot_key)
+  
+%%%%%%% inputs %%%%%%%%
+% n - number of frequencies
+% fmean - mean frequency
+% fs - sample frequency
+% plot_key - 1 for plot, 0 for no plot
+% freq
+tdur=1/fmean; 
+ts = tdur/fs; 
+f = (fmean/2)*(randn(nfreqs,1)) + fmean;
+fvec = []; 
+for i=1:nfreqs 
+    fvec = [fvec , f(i)*ones(1,fs)]; 
+end
+% algo
+fac_old = 0; 
+for i=1:length(fvec)
+    fac = fac_old + fvec(i)*ts; 
+    y(i) = sin(2*pi*fac); 
+    fac_old = fac; 
+end
+% plot
+if plot_key == 1
+subplot(211) 
+    plot(0:tdur:tdur*(nfreqs-1),f,'k.',[0 tdur*nfreqs],fmean/2*[1 1],[0 tdur*nfreqs],fmean*[1.5 1.5]), ylim([0.25 1.75]*fmean)
+subplot(212)
+    plot(0:ts:ts*(length(y)-1),y)
+end
+end

### 2014-05-21 Matlab/Time_varying_sinewave.m
updated time_varying_sinwave to return frequencies

@@ -1,10 +1,8 @@
-function [TDSignal, TDPhase, Time] = Time_varying_sinewave(CentralFreq, STDFreq, Order, Length, DT, Graphic)
-%% time varying signal
-%[Signal] = Time_varying_sinewave(CentralFreq, STDFreq, Order, Length)
-  
-  % options
+function [TDSignal, TDPhase, Time, Freqs] = Time_varying_sinewave(CentralFreq, STDFreq, Order, Length, DT, Graphic)
+%[TDSignal, TDPhase, Time, Freqs] = Time_varying_sinewave(CentralFreq, STDFreq, Order, Length, DT, Graphic)
+%
+%%
 Time = 0:DT:Length;
-% freq
 f = STDFreq*randn(Order,1) + CentralFreq;
 TDSignal = [];
 TDPhase = [];
@@ -18,6 +16,7 @@ for N = 1:Order
 end
 if length(Time)<length(TDSignal)
     fprintf('The specified length was too short \nto accomodate the order and sampling frequency.\n Length was changed to %d\n',length(TDSignal))
+    Time = (0:length(TDSignal)-1);
 else
     while length(Time)>length(TDSignal)
        TDSignal = [TDSignal,TDSignal];
@@ -35,4 +34,6 @@ if Graphic
         plot(TDSignal)
     linkaxes([ax1 ax2],'x')
 end
+
+Freqs=(Time./(length(Time)))./DT;
 end

### 2014-05-21 Manuscript/Phase_detectors_outline.tex
update outline Jess

@@
 
-\subsection*{Time-averaged phase}
+\subsection*{Time-averaged phase, or Frequency domain phase}
 
@@
 Regulation of one variable by another can result in a positive phase while time delays can cause negative phase.
+
+\section*{When each method can fail}
+\begin{itemize}
+\item Frequency domain phase difference can fail when one oscillation leads another by more than half of a cycle.
+\item Time-domain phase is only accessible at one frequency at a time if the Hilbert transform is used
+\item Time-domain phase must have \textit{some} problems if wavelet 
+\end{itemize}
 
@@
 \item cerebral blood flow
+\item JESS
 \end{itemize}
@@
 
+\section*{Results}
+
+	\subsection*{Figures}
+	\begin{enumerate}
+	\item Simulation
+		\begin{enumerate}
+		\item Time series of raw simulated data + added noise
+		\item Power spectrum of the data
+		\item Time-domain phase 
+		\item Accuracy of each detector at a range of signal to noise ratios
+		\end{enumerate}
+	\item Rat data
+		\begin{enumerate}
+		\item BP and cortical perfusion
+		\item Phase interactions between two or three regions on the renal surface
+		\end{enumerate}
+	\item{Human data}
+		\begin{enumerate}
+		\item BP and heart rate
+		\item Use phase to find the lag between a change in bp and a change in heart rate
+		\end{}
+	\end{enumerate}
+
 \end{document}

### 2014-05-21 Matlab/wavelet_interp.m
Normalized the wavelet_interp function for inputs and outputs

@@ -1,27 +1,37 @@
-function [freq,power,WN,scales,phase_max_u,phase_max_w,wi] =  wavelet_interp(x)
-
-res=256; %frequency resolution
-dt=1; %sampling rate
-dj=0.0625; %wavelet interval
+function [TDPhase] =  wavelet_interp(TDSignal, DT, Graphic)
+%%
+Time = 0:length(TDSignal)-1;
+Time=Time.*DT;
+dj=0.04; %wavelet interval
 J1=127; %total # of scales
 pad=1; %zero-pad signals
-s0=2*dt; %set initial scale
+s0=0.5; %set initial scale
 mother='Morlet'; %wavelet shape
 param=6; %initial wavelet order
 
 %computes the wavelets
-[WN,~,scales] = wavelet(x,dt,pad,dj,s0,J1,mother,param);
-freq=1./(1.033*scales);
-power = abs(WN).^2;
-
-siz = size(power,2);
-
-for k = 1:siz
-    [~,idx(k)] = max(power(:,k));
-    phase_max(k) = angle(WN(idx(k),k));
+[WN,Period,~] = wavelet(TDSignal,DT,pad,dj,s0,J1,mother,param);
+Power = abs(WN).^2;
+%Freqs=1./(1.033.*Scale);
+if Graphic
+    figure(1);clf;
+    mesh(Time, Period, Power) 
+    view(45,90);
+    colormap(hot)
 end
-phase_max_u = unwrap(phase_max)';
-phase_max_w = wrapToPi(phase_max_u)';
-
-wi = (diff(phase_max_u).*2*2/pi)';
+%%
+Size = size(Power,2);
+Phase_max = zeros(Size,1);
+for k = 1:Size
+    [~,TempPeriod] = max(Power(:,k));
+    Phase_max(k) = angle(WN(TempPeriod,k));
+end
+Phase_max_u = unwrap(Phase_max)';
+size(Phase_max)
+TDPhase = wrapToPi(Phase_max_u)';
+if Graphic
+   figure(2); clf
+   plot(TDPhase);
+end
+%wi = (diff(Phase_max_u).*2*2/pi)';
 end

### 2014-05-21 Manuscript/Phase_detectors_outline.tex
new title
add notes on BP-HR phase lag

@@
 \documentclass{article}
-\title{Phase paper outline}
+\title{Phase paper outline your mom last night}
 \author{}
@@
 \item Noise and time-variance present in physiological data makes this process more difficult.
+
+\item In addition to finding the individual phase of an oscillating signal, determination of phase shift, or lag-time, between two related signals is an important physiological parameter that may offer insight into pathophysiological conditions.
 \item The goal of this paper is to identify the most accurate methods of extracting phase information and determine how to deal with common hurdles present in physiological data.
@@
 	\end{itemize}
-\item BP and Heart rate
+\item Blood pressure and heart rate
 	\begin{itemize}
-	\item phase lag between changes in heart rate and changes in BP
+	\item [Phase lag between changes in blood pressure and changes in heart rate] \hfill \\
+	The oscillations of blood pressure and heart rate are often compared using cross-spectral analyses to quantify baroreflex function.
+With this method, the coherence, transfer function gain, and phase relationship between the two signals are quantified.
+The phase shift between blood pressure and heart rate is lengthened in some pathophysiological conditions (Javorka et al, 2011) and more variable/unstable in other conditions (Halamek et al, 2003 Circulation).
+Therefore, the phase relationship between these two signals might be an important outcome measure for cardiovascular testing.
 	\end{itemize}
-\item Something about SCG or ECG
-\item cerebral blood flow
-\item JESS
+\item Something about SCG or ECG ?
+\item Cerebral blood flow ?
 \end{itemize}
@@
 		\item Use phase to find the lag between a change in bp and a change in heart rate
-		\end{}
+		\end{enumerate}
 	\end{enumerate}

### 2014-05-21 Matlab/hilbert_interp.m
improved plot and inputs

@@ -1,14 +1,38 @@
-function [phh,phhu,phhw,w,wi] =  hilbert_interp(x)
+function [phh,phhu,phhw,w,wi] =  hilbert_interp(Signal,Dt,f1,f2,Graphic)
+%% Hilbert Interp %%
+% function purpose is to use the hilbert transform of a signal and estimate
+% the instantaneous phase and frequency of the signal
+%%%%%%%%%% Inputs %%%%%%%%%%
+% Signal - the time domain signal to be analyzed
+% Dt - Time step for the signal i.e. 1/sample frequency
+% f1 - lower bound of the frequency range for the oscillation of interest
+% f2 - upper bound for the frequency range of the oscillation of interest
+% Graphic - 1 for plots, 0 for no plots
+%%%%%%%%%% Outputs %%%%%%%%%%
+% phh - Instantaneous phase wrapped to 2pi
+% phhu - Instantaneous phase unwrapped
+% phhw - Instantaneous unwrapped phase rewrapped to Pi
+% w = Instantaneous frequency
+% wi = Instantaneous frequency with phase slipes interpolated
 
+Fs = 1/Dt;  % Sampling Frequency
+%FOR MYO
+N   = 6;    % Order
+% Construct an FDESIGN object and call its BUTTER method.
+h  = fdesign.bandpass('N,F3dB1,F3dB2', N, f1, f2, Fs);
+Hd = design(h, 'butter');
+[b,a]=sos2tf(Hd.sosMatrix,Hd.ScaleValues);
 
-xh = hilbert(x);
+Signal_f = filtfilt(b,a,Signal); %bandpass filter the input signal
+
+xh = hilbert(Signal_f);
 phh = angle(xh);
 phhu = unwrap(phh);
 
     w = diff(phhu).*(2*2/pi);
     wi = w;
-%%
-t = 1:length(x);
+%% find data points where inst. frequency is outside filter pass band, and interpolate across those points
+t = Dt:Dt:length(Signal_f)*Dt;
 k1=find(wi<0);
 kk1=[k1;k1+1;k1-1];
 kk1(kk1<=0)=[];
@@ -17,11 +41,31 @@ ti=t(2:end);
 tt=ti;
 tt(kk1)=[];
 wi(kk1)=[];
-wi=interp1(tt,wi,ti,'linear','extrap');
[…]

### 2014-05-21 Manuscript/Phase_detectors_outline.tex
added to intro

--- 2014-05-21 Manuscript/Phase_detectors_outline.tex
@@
 
+Homeostasis is maintained by numerous interacting physiological control systems.
+Physiological systems are responsible for controlling a given output variable in response to one or more input variables.
+For example Heart rate is controlled by the autonomic nervous system to maintain blood pressure.
+Nonlinear responses between input and output in physiological systems are ubiquitous.
+Furthermore there are inherent delays in the response of each system because of inter and intra cellular signalling events.
+These nonlinearities
+
 \section*{Methods}

### 2014-05-21 Manuscript/Phase_detectors_outline.tex
added to intro

--- 2014-05-21 Manuscript/Phase_detectors_outline.tex
@@
 \documentclass{article}
-\title{Phase paper outline your mom last night}
+\title{Phase paper outline}
 \author{}

### 2014-05-22 Manuscript/Phase_detectors_outline.tex
add citation for phase variability

--- 2014-05-21 Manuscript/Phase_detectors_outline.tex
@@
 With this method, the coherence, transfer function gain, and phase relationship between the two signals are quantified.
-The phase shift between blood pressure and heart rate is lengthened in some pathophysiological conditions (Javorka et al, 2011) and more variable/unstable in other conditions (Halamek et al, 2003 Circulation).
-Therefore, the phase relationship between these two signals might be an important outcome measure for cardiovascular testing.
+The phase shift between blood pressure and heart rate is lengthened in some pathophysiological conditions (Javorka et al, 2011) and more variable/unstable in other conditions (Halamek et al, 2003 Circulation; Stewart et al., 2000).
+Therefore, the phase relationship between these two signals is an important outcome measure for cardiovascular testing.
 	\end{itemize}

### 2014-05-22 Matlab/Generate_TV_signal.m
TV signal

@@ -1,18 +1,18 @@
 %%% generate TV signal %%%
 
-f1 = 0.04; %low frequency
-f2 = 0.1; % high frequency
+f1 = 0.1; %low frequency
+f2 = 0.3; % high frequency
 len = 500; % duration in seconds
 AM = 1; % amplitude modulation 
-FM = 1; % frequency modulation
-noi = 1; % add GWN
+FM = 0; % frequency modulation
+noi = 0; % add GWN
 t = 1:len;
 
 [x]=test_sig_AMFM(f1,f2,len,AM,FM,noi);
 
 
  
-res=256; %frequency resolution
+% res=256; %frequency resolution
 dt=1; %sampling rate
 dj=0.0625; %wavelet interval
 J1=127; %total # of scales
@@ -20,8 +20,10 @@ pad=1; %zero-pad signals
 s0=2*dt; %set initial scale
 mother='Morlet'; %wavelet shape
 param=6; %initial wavelet order
-az = 63;
-el = 46;
+% az = 63;
+% el = 46;
+az = 45;
+el = 90;
 
 %computes the wavelets
 [WN1,~,scales] = wavelet(x,dt,pad,dj,s0,J1,mother,param);
@@ -30,6 +32,7 @@ power = abs(WN1).^2;
 
 mesh(t,freq,power)
 view(az,el)
+colormap(hot)
 xlabel('Time (s)')
 ylabel('Frequency (Hz)')
 zlabel('Power (Units^2/Hz)')

### 2014-05-22 Matlab/Time_varying_sinewave.m
updated commit

@@ -11,8 +11,9 @@ for N = 1:Order
     TempTime = 0:Period-1;
     TempSignal=cos(TempTime/Period*2*pi);
     TDSignal = [TDSignal,TempSignal];
-    TempPhase = 0:2*pi/length(TempTime):2*pi-2*pi/length(TempTime);
-    TDPhase = [TDPhase,TempPhase];
+    TempPhase = 0:2*pi/length(TempTime):pi;
+    TempPhase2 = -pi:2*pi/length(TempTime):0-2*pi/length(TempTime);
+    TDPhase = [TDPhase,TempPhase,TempPhase2];
 end
 if length(Time)<length(TDSignal)
     fprintf('The specified length was too short \nto accomodate the order and sampling frequency.\n Length was changed to %d\n',length(TDSignal))

### 2014-05-23 Manuscript/Phase_detectors_outline.tex
Added a bibliography. Added a Tables subsection to the outline. The Muller folder is a bullshit temp folder but I am too lazy to deal with it now.

--- 2014-05-21 Manuscript/Phase_detectors_outline.tex
@@
 \subsection*{Potential physiology journals}
-
+The paper should have this structure:\cite{muller_estimation_2003}
 \begin{itemize}
@@
 \item Journal of experimental physiology
+\item Journal of Applied Phyiology
+\item E-Life
 \end{itemize}
@@
 \end{itemize}
-
-Homeostasis is maintained by numerous interacting physiological control systems.
-Physiological systems are responsible for controlling a given output variable in response to one or more input variables.
-For example Heart rate is controlled by the autonomic nervous system to maintain blood pressure.
-Nonlinear responses between input and output in physiological systems are ubiquitous.
-Furthermore there are inherent delays in the response of each system because of inter and intra cellular signalling events.
-These nonlinearities
 
@@
 
+	\subsection*{Tables}
+		\begin{enumerate}
+			\item Simulation
+			\begin{enumerate}
+			\item Noise conversation
+				\begin{itemize}
+					\item Add gaussian noise from snr=$\infty$ up to when it breaks down.
+					\item It breaks down when 0 is not in the 95\% confidence interval of Bland-Altman-style statistics.		
+				\end{itemize}
+			\item Chirp (Frequency from point A to point B)
+				\begin{itemize}
+					\item Specifically to talk about limits to the bandpass filtering needed for the Hilbert method.
+				\end{itemize}
+			\item Length of signal
+				\begin{itemize}
+					\item Shorten the signal until techniques breakdown.
+					\item Relative to frequency.
+				\end{itemize}		
+			\end{enumerate}
+			\item Physiological Data
+
+		\end{enumerate}
+
+\bibliographystyle{plain}
+\bibliography{OutlineBib}
+
 \end{document}

### 2014-05-23 Manuscript/Muller/files/297/9CC.js

@@ -1,0 +1,56 @@
+// Qualaroo for springer.com
+// (C) 2013 Qualaroo. All rights reserved.
+// qualaroo.com
+
+//$ site: 39334, generated: 2013-09-17 12:59:31 UTC
+//$ type: base, rev. 89262e9d (deploy)
+
+if(typeof _kiq == 'undefined'){ var _kiq=[]; }
+if(typeof KI == 'undefined' && (function(a,d){
+  if(typeof KI_NOCHECK != 'undefined')
+    return 1;
+  if(a.match(/(MSIE [7,8,9,10])|(Firefox\/([3-9]|10|11|12|13|14|15|16|17|18|19|20|21|22|23|24|25))|(Opera\/[9])|Safari|Chrome/i)) {
+    if(a.match(/ipad/i))
+      return 1;
+    if(a.match(/msie/i) && d.compatMode == 'BackCompat')
+      return 0;
+    if(a.match(/(phone|mobile)/i))
+      return 0;
+    return 1;
+  }
+})(navigator.userAgent, document) == 1) {
+var $KI={version:3,s3:"s3.amazonaws.com",bucket:'ki.js',preflight:$KI||{},guid:function(){function s(){return(((1+Math.random())*65536)|0).toString(16).substring(1)}return(s()+s()+"-"+s()+"-"+s()+"-"+s()+"-"+s()+s()+s())},css:function(css){var c=css.replace(/images\//gi,(($KI.preflight.images)?$KI.preflight.images:"//"+[$KI.s3,$KI.bucket,"images",$KI.version].join("/")+"/"));var t=new $KI.$("style",null,{type:"text/css"});if(t.styleSheet){t.styleSheet.cssText=c}else{t.appendChild(document.createTextNode(c))}document.body.appendChild(t);return t},ready:function(func,bind){var ran=false;function proxy(){if(ran){return false}ran=true;func.apply(bind)}function check(){var r=document.readyState;if(r=="complete"||r=="loaded"||r=="interactive"){proxy();return true}return false}if(!check()){if(document.addEventListener){document.addEventListener("DOMContentLoaded",proxy,true);document.addEventListener("readystatechange",check,true);window.addEventListener("load",proxy,true)}else{if(document.attachEvent){document.attachEvent("onreadystatechange",check);window.attachEvent("onload",proxy)}}}}
[…]

### 2014-05-23 Manuscript/Muller/files/297/all.js

@@ -1,0 +1,22 @@
+window.Modernizr=function(ap,ao,an){function I(b){ah.cssText=b}function aa(d,c){return I(ae.join(d+";")+(c||""))}function Y(d,c){return typeof d===c}function W(d,c){return !!~(""+d).indexOf(c)}function U(f,c){for(var h in f){var g=f[h];if(!W(g,"-")&&ah[g]!==an){return c=="pfx"?g:!0}}return !1}function S(g,c,k){for(var j in g){var h=c[g[j]];if(h!==an){return k===!1?g[j]:Y(h,"function")?h.bind(k||c):h}}return !1}function Q(g,f,k){var j=g.charAt(0).toUpperCase()+g.slice(1),h=(g+" "+ac.join(j+" ")+j).split(" ");return Y(f,"string")||Y(f,"undefined")?U(h,f):(h=(g+" "+ab.join(j+" ")+j).split(" "),S(h,f,k))}function O(){al.input=function(f){for(var b=0,a=f.length;b<a;b++){V[f[b]]=f[b] in ag}return V.list&&(V.list=!!ao.createElement("datalist")&&!!ap.HTMLDataListElement),V}("autocomplete autofocus list placeholder max min multiple pattern required step".split(" "))}var am="2.6.2",al={},ak=ao.documentElement,aj="modernizr",ai=ao.createElement(aj),ah=ai.style,ag=ao.createElement("input"),af={}.toString,ae=" -webkit- -moz- -o- -ms- ".split(" "),ad="Webkit Moz O ms",ac=ad.split(" "),ab=ad.toLowerCase().split(" "),Z={},X={},V={},T=[],R=T.slice,P,N=function(w,u,t,s){var r,q,p,o,g=ao.createElement("div"),f=ao.body,b=f||ao.createElement("body");if(parseInt(t,10)){while(t--){p=ao.createElement("div"),p.id=s?s[t]:aj+(t+1),g.appendChild(p)}}return r=["&#173;",'<style id="s',aj,'">',w,"</style>"].join(""),g.id=aj,(f?g:b).innerHTML+=r,b.appendChild(g),f||(b.style.background="",b.style.overflow="hidden",o=ak.style.overflow,ak.style.overflow="hidden",ak.appendChild(b)),q=u(g,w),f?g.parentNode.removeChild(g):(b.parentNode.removeChild(b),ak.style.overflow=o),!!q},M=function(){function c(h,g){g=g||ao.
[…]

### 2014-05-23 Manuscript/Phase_detectors_outline.tex
Added bibliography

@@
 \item Signal transduction, be it physical signals like pressure or cellular signals like phosphorylation, introduces a delay between input and output. 
-\item Non-linearities and delays conspire to generate oscillations in physiological control systems, for example oscillations in renal blood flow, or oscillations in cerebral blood flow.
+\item Non-linearities and delays \cite{ottesen_modelling_1997} conspire to generate oscillations in physiological control systems, for example oscillations in renal blood flow, or oscillations in cerebral blood flow.
 \item Oscillating physiological systems can become synchronized if they are somehow physically coupled. For example, sinus arrhythmia caused by respiration. 

### 2014-05-23 Manuscript/Muller/files/297/9CC.js

@@ -1,56 +1,0 @@
-// Qualaroo for springer.com
-// (C) 2013 Qualaroo. All rights reserved.
-// qualaroo.com
-
-//$ site: 39334, generated: 2013-09-17 12:59:31 UTC
-//$ type: base, rev. 89262e9d (deploy)
-
-if(typeof _kiq == 'undefined'){ var _kiq=[]; }
-if(typeof KI == 'undefined' && (function(a,d){
-  if(typeof KI_NOCHECK != 'undefined')
-    return 1;
-  if(a.match(/(MSIE [7,8,9,10])|(Firefox\/([3-9]|10|11|12|13|14|15|16|17|18|19|20|21|22|23|24|25))|(Opera\/[9])|Safari|Chrome/i)) {
-    if(a.match(/ipad/i))
-      return 1;
-    if(a.match(/msie/i) && d.compatMode == 'BackCompat')
-      return 0;
-    if(a.match(/(phone|mobile)/i))
-      return 0;
-    return 1;
-  }
-})(navigator.userAgent, document) == 1) {
-var $KI={version:3,s3:"s3.amazonaws.com",bucket:'ki.js',preflight:$KI||{},guid:function(){function s(){return(((1+Math.random())*65536)|0).toString(16).substring(1)}return(s()+s()+"-"+s()+"-"+s()+"-"+s()+"-"+s()+s()+s())},css:function(css){var c=css.replace(/images\//gi,(($KI.preflight.images)?$KI.preflight.images:"//"+[$KI.s3,$KI.bucket,"images",$KI.version].join("/")+"/"));var t=new $KI.$("style",null,{type:"text/css"});if(t.styleSheet){t.styleSheet.cssText=c}else{t.appendChild(document.createTextNode(c))}document.body.appendChild(t);return t},ready:function(func,bind){var ran=false;function proxy(){if(ran){return false}ran=true;func.apply(bind)}function check(){var r=document.readyState;if(r=="complete"||r=="loaded"||r=="interactive"){proxy();return true}return false}if(!check()){if(document.addEventListener){document.addEventListener("DOMContentLoaded",proxy,true);document.addEventListener("readystatechange",check,true);window.addEventListener("load",proxy,true)}else{if(document.attachEvent){document.attachEvent("onreadystatechange",check);window.attachEvent("onload",proxy)}}}}
[…]

### 2014-05-23 Manuscript/Muller/files/297/all.js

@@ -1,22 +1,0 @@
-window.Modernizr=function(ap,ao,an){function I(b){ah.cssText=b}function aa(d,c){return I(ae.join(d+";")+(c||""))}function Y(d,c){return typeof d===c}function W(d,c){return !!~(""+d).indexOf(c)}function U(f,c){for(var h in f){var g=f[h];if(!W(g,"-")&&ah[g]!==an){return c=="pfx"?g:!0}}return !1}function S(g,c,k){for(var j in g){var h=c[g[j]];if(h!==an){return k===!1?g[j]:Y(h,"function")?h.bind(k||c):h}}return !1}function Q(g,f,k){var j=g.charAt(0).toUpperCase()+g.slice(1),h=(g+" "+ac.join(j+" ")+j).split(" ");return Y(f,"string")||Y(f,"undefined")?U(h,f):(h=(g+" "+ab.join(j+" ")+j).split(" "),S(h,f,k))}function O(){al.input=function(f){for(var b=0,a=f.length;b<a;b++){V[f[b]]=f[b] in ag}return V.list&&(V.list=!!ao.createElement("datalist")&&!!ap.HTMLDataListElement),V}("autocomplete autofocus list placeholder max min multiple pattern required step".split(" "))}var am="2.6.2",al={},ak=ao.documentElement,aj="modernizr",ai=ao.createElement(aj),ah=ai.style,ag=ao.createElement("input"),af={}.toString,ae=" -webkit- -moz- -o- -ms- ".split(" "),ad="Webkit Moz O ms",ac=ad.split(" "),ab=ad.toLowerCase().split(" "),Z={},X={},V={},T=[],R=T.slice,P,N=function(w,u,t,s){var r,q,p,o,g=ao.createElement("div"),f=ao.body,b=f||ao.createElement("body");if(parseInt(t,10)){while(t--){p=ao.createElement("div"),p.id=s?s[t]:aj+(t+1),g.appendChild(p)}}return r=["&#173;",'<style id="s',aj,'">',w,"</style>"].join(""),g.id=aj,(f?g:b).innerHTML+=r,b.appendChild(g),f||(b.style.background="",b.style.overflow="hidden",o=ak.style.overflow,ak.style.overflow="hidden",ak.appendChild(b)),q=u(g,w),f?g.parentNode.removeChild(g):(b.parentNode.removeChild(b),ak.style.overflow=o),!!q},M=function(){function c(h,g){g=g||ao.
[…]

### 2014-05-23 Manuscript/Phase_detectors_outline.tex
Updated the bibliography with some of Jess' stuff (might totally be wrong). Added BlandAltman function to Matlab folder.

@@
 \item Short time Fourier transform
-\item Hilbert transform
-\item Wavelet transform 
+\item Hilbert transform \cite{muller_estimation_2003}
+\item Wavelet transform \cite{farge_wavelet_1992,torrence_practical_1998}
 \end{itemize}
@@
 	\item Each phase detector was used to determine the instantaneous phase of each frequency band isolated from the simulated data
-	\item The accuracy of the estimated instantaneous phase was calculated as ???
+	\item The accuracy of the estimated instantaneous phase will be calculated using Bland-Altman statistics.
+The closet mean to zero wins.
+Techniques are deemed as broken when zero is not within $\overline{u}\pm1.96\sigma$
 	\end{itemize}
@@
 	\begin{itemize}
-	\item [Phase lag between changes in blood pressure and changes in heart rate] \hfill \\
-	The oscillations of blood pressure and heart rate are often compared using cross-spectral analyses to quantify baroreflex function.
+	\item Phase lag between changes in blood pressure and changes in heart rate
+
+	\item The oscillations of blood pressure and heart rate are often compared using cross-spectral analyses to quantify baroreflex function.
 With this method, the coherence, transfer function gain, and phase relationship between the two signals are quantified.
-The phase shift between blood pressure and heart rate is lengthened in some pathophysiological conditions (Javorka et al, 2011) and more variable/unstable in other conditions (Halamek et al, 2003 Circulation; Stewart et al., 2000).
+The phase shift between blood pressure and heart rate is lengthened in some pathological conditions \cite{tonhajzerova_cardiac_2011} and more variable/unstable in other conditions (\cite{halamek_variability_2003}; Stewart et al., 2000).
 Therefore, the phase relationship between these two signals is an important outcome measure for cardiovascular testing.

### 2014-05-23 Matlab/BlandAltman.m

@@ -1,0 +1,26 @@
+function [Mean,U,Plot] = BlandAltman(V1,V2, Graphic)
+%[Mean,U,Plot] = BlandAltman(V1,V2)
+%You want to follow up a call to this function by something like
+%   figure(11); clf; plot(Plot(1,:),Plot(2,:),'*');title('MCs')
+%   hold on; plot([min(Plot(1,:)) max(Plot(1,:))],[Mean Mean],'k');
+%   plot([min(Plot(1,:)) max(Plot(1,:))],[U U],'k');
+%   plot([min(Plot(1,:)) max(Plot(1,:))],[-U -U],'k'); hold off;
+%%
+Size = size(V1);
+if Size(1)>Size(2)
+    V1=V1';
+    V2=V2';
+end
+%%
+Mean=(mean(V1-V2));
+U=abs(1.96*(std(V1-V2)));
+Plot=[(V1+V2)./2; (V1-V2)];
+%%
+if Graphic
+    figure(11); clf; plot(Plot(1,:),Plot(2,:),'*');
+    hold on; plot([min(Plot(1,:)) max(Plot(1,:))],[Mean Mean],'k');
+    plot([min(Plot(1,:)) max(Plot(1,:))],[Mean+U Mean+U],'k');
+    plot([min(Plot(1,:)) max(Plot(1,:))],[Mean-U Mean-U],'k'); hold off;
+end
+end
+

### 2014-06-02 Matlab/Phase_detectors_compare_run.m
compare Hilbert to Wavelet

@@ -1,0 +1,54 @@
+function [MeanDiff_Wave,MeanDiff_Hilb,STDDiff_Wave,STDDiff_Hilb] = Phase_detectors_compare_run(CentralFreq,STDFreq,Order,Length,DT,Graphic,SNRMin,SNRMax,NoiseSteps)
+%% Make original test signal
+CentralFreq = 0.5;
+STDFreq = CentralFreq*0.2;
+Order = 3;
+Length = 1000;
+DT = 0.1;
+Graphic = 0;
+
+[TDSignal, ~, TDPhaseUnwrap, Time, ~] = Time_varying_sinewave(CentralFreq, STDFreq, Order, Length, DT, Graphic);
+
+% Add noise to test signal
+SNRMin = -10;
+SNRMax = 10;
+NoiseSteps = 21;
+NoiseVec = linspace(SNRMin,SNRMax,NoiseSteps);
+
+for k = 1:NoiseSteps
+    GWNSignal(:,k) = awgn(TDSignal,NoiseVec(k),'measured');
+end
+
+% Estimate phase with hilbert transform
+f1 = CentralFreq-(0.5*CentralFreq);
+f2 = CentralFreq+(0.5*CentralFreq);
+
+
+TDPhase_Hilb =  hilbert_interp(TDSignal,DT,f1,f2,Graphic);
+
+for k = 1:NoiseSteps
+    GWNPhase_Hilb(:,k) = hilbert_interp(GWNSignal(:,k),DT,f1,f2,Graphic);
+end
+% Estimate phase with wavelet transform
+
+TDPhase_Wave =  wavelet_interp(TDSignal, DT, Graphic);
+
+for k = 1:NoiseSteps
+    GWNPhase_Wave(:,k) = wavelet_interp(GWNSignal(:,k), DT, Graphic);
+end
+
+%% Determine agreement between each estimate and the true phase (Bland-Altman)
+Graphic = 0;
+% for noise free signals
+[Difference_Hilb1,MeanEst_Hilb1,MeanDiff_Hilb1,STDDiff_Hilb1] = BlandAltman(TDPhaseUnwrap,TDPhase_Hilb',Graphic);
+[Difference_Wave1,MeanEst_Wave1,MeanDiff_Wave1,STDDiff_Wave1] = BlandAltman(TDPhaseUnwrap,TDPhase_Wave,Graphic);
[…]

### 2014-06-03 Matlab/Phase_detectors_compare_trials.m
repeat Hilbert vs wavelet multiple times

@@ -1,0 +1,32 @@
+clear all;
+clc
+%%
+tic
+
+CentralFreq = 0.5;
+STDFreq = CentralFreq*0.05;
+Order = 4;
+Length = 1000;
+DT = 0.1;
+Graphic = 0;
+
+SNRMin = -10;
+SNRMax = 10;
+NoiseSteps = 21;
+NoiseVec = linspace(SNRMin,SNRMax,NoiseSteps);
+
+
+Trials = 20;
+
+for k = 1:Trials
+    [MeanDiff_Wave(k,:),MeanDiff_Hilb(k,:),STDDiff_Wave(k,:),STDDiff_Hilb(k,:)] = Phase_detectors_compare_run(CentralFreq,STDFreq,Order,Length,DT,Graphic,SNRMin,SNRMax,NoiseSteps);
+end
+
+toc
+%% 
+for k = 1:Trials
+plot(NoiseVec,MeanDiff_Hilb(k,:),'k.',NoiseVec,MeanDiff_Wave(k,:),'ro'); hold on
+xlabel 'SNR (dB)'
+ylabel 'Estimate - True'
+legend('Hilbert','Wavelet')
+end

### 2014-06-03 Matlab/Phase_detectors_plots.m
make tfour plots of the data

@@ -1,0 +1,36 @@
+%% Plot TDSignal
+figure(1)
+plot(Time,TDSignal,'k-')
+xlim([0 100])
+ylim([-1.2 1.2])
+xlabel 'Time (s)'
+ylabel 'Amplitude'
+title 'Original signal'
+
+%% Plot True, Hilbert and Wavelet Phase
+figure(2)
+plot(Time,TDPhaseUnwrap,'k-',Time,unwrap(TDPhase_Hilb),'bo',Time,TDPhase_Wave,'ro')
+xlim([0 100])
+axes('Position',[0.6,0.2,0.3,0.3])
+box on
+xs = 100;
+xe = 120;
+plot(Time(xs:xe),TDPhaseUnwrap(xs:xe),'k-',Time(xs:xe),TDPhase_Hilb(xs:xe),'bo',Time(xs:xe),TDPhase_Wave(xs:xe),'ro')
+axis tight
+
+%% Bland-Altman plot for noise-free signal
+figure(3)
+plot(MeanEst_Hilb1,Difference_Hilb1,'k-',MeanEst_Wave1,Difference_Wave1,'ro')
+ylim([-0.5 0.5])
+title 'Bland-Altman plot'
+xlabel 'Mean Estimated phase'
+ylabel 'Difference (Estimated phase - True phase)'
+legend('Hilbert','Wavelet')
+
+%% Figure for Bland-Altman after trials at multiple SNR
+for k = 1:Trials
+plot(NoiseVec,MeanDiff_Hilb(k,:),'k.',NoiseVec,MeanDiff_Wave(k,:),'ro'); hold on
+xlabel 'SNR (dB)'
+ylabel 'Estimate - True'
+legend('Hilbert','Wavelet')
+end

### 2014-06-05 Matlab/Phase_detectors_compare_run.m
comopare HIlbert and Wavelet

@@ -1,18 +1,18 @@
-function [MeanDiff_Wave,MeanDiff_Hilb,STDDiff_Wave,STDDiff_Hilb] = Phase_detectors_compare_run(CentralFreq,STDFreq,Order,Length,DT,Graphic,SNRMin,SNRMax,NoiseSteps)
+function [Time,TDSignal,TDPhaseUnwrap,TDPhase_Hilb,TDPhase_Wave,Difference_Hilb1,MeanEst_Hilb1,MeanDiff_Hilb1,STDDiff_Hilb1,Difference_Wave1,MeanEst_Wave1,MeanDiff_Wave1,STDDiff_Wave1,Difference_Hilb,MeanEst_Hilb,MeanDiff_Hilb,STDDiff_Hilb,Difference_Wave,MeanEst_Wave,MeanDiff_Wave,STDDiff_Wave] = Phase_detectors_compare_run(CentralFreq,STDFreq,Order,Length,DT,Graphic,SNRMin,SNRMax,NoiseSteps)
 %% Make original test signal
-CentralFreq = 0.5;
+CentralFreq = 0.2;
 STDFreq = CentralFreq*0.2;
-Order = 3;
-Length = 1000;
+Order = 8;
+Length = 100;
 DT = 0.1;
 Graphic = 0;
 
 [TDSignal, ~, TDPhaseUnwrap, Time, ~] = Time_varying_sinewave(CentralFreq, STDFreq, Order, Length, DT, Graphic);
 
 % Add noise to test signal
-SNRMin = -10;
-SNRMax = 10;
-NoiseSteps = 21;
+% SNRMin = -10;
+% SNRMax = 10;
+% NoiseSteps = 21;
 NoiseVec = linspace(SNRMin,SNRMax,NoiseSteps);
 
 for k = 1:NoiseSteps
@@ -37,7 +37,7 @@ for k = 1:NoiseSteps
     GWNPhase_Wave(:,k) = wavelet_interp(GWNSignal(:,k), DT, Graphic);
 end
 
-%% Determine agreement between each estimate and the true phase (Bland-Altman)
+% Determine agreement between each estimate and the true phase (Bland-Altman)
 Graphic = 0;
 % for noise free signals
 [Difference_Hilb1,MeanEst_Hilb1,MeanDiff_Hilb1,STDDiff_Hilb1] = BlandAltman(TDPhaseUnwrap,TDPhase_Hilb',Graphic);

### 2014-06-05 Matlab/Phase_detectors_compare_trials.m
run multiple trials of phase estimates

@@ -1,32 +1,121 @@
-clear all;
+%%%%%%%%%%%%%% Phase detector simulation %%%%%%%%%%%%%%
+% This script calls multiple other functions in order to make a series of sine waves
+% with multiple frequencies and increasing levels of noise. The phase of each wave
+% is then esimated with Wavelet and Hilbert transforms and their agreement wih the
+% true phase of the original noise-free wave is shown with a Bland-Altman plot. Then
+% the average agreement is shown at each noise level over multiple repetitions.
+
+%%%%%%%%%%%% Inputs %%%%%%%%%%%% 
+% CentralFreq - the central frequency of the sine wave
+% STDFreq - standard deviation of the frequecy over time
+% Order - the number of frequencies used in the wave
+% Length - Duration of the wave in seconds
+% DT - Time step of the wave, equal to 1/sample frequency
+% Graphic - 1 for plots, 0 for no plots
+% SNRMin - minimum signal to noise ratio in dB
+% SNRMax - maximum signal to noise ratio
+% NoiseSteps - number of individual signal to noise ratios to test
+% Trials - Number of times to repeat the analysis
+
+%%%%%%%%%%%% Outputs %%%%%%%%%%%% 
+
+% TDSignal - Original sine wave with no noise
+% TDPhaseUnwrap - True phase of TDSignal
+% TDPhase_Hilb - Estimated phase with Hilbert method
+% TDPhase_Wave - Estimated phase with Wavelet method
+% Difference_Hilb1 - Difference between true phase and Hilbert estimated phase without noise
+% MeanEst_Hilb1 - Mean of True phase and Hilbert estimated phase
+% Difference_Wave1 - Difference between true phase and Wavelet estimated phase without noise
+% MeanEst_Wave1 - Mean of True phase and Wavelet estimated phase
+
+clear all
+close all
 clc
 %%
 tic
 
[…]

### 2014-06-05 Matlab/BlandAltman.m
run Bland-Altmanon two sets of data

@@ -1,0 +1,18 @@
+function [Difference,MeanEst,MeanDiff,STDDiff] = BlandAltman(Sig1,Sig2,Graphic)
+
+
+EstPhases = [Sig1; Sig2]';
+
+MeanEst = mean(EstPhases,2);
+
+Difference = Sig1 - Sig2;
+
+MeanDiff = mean(Difference);
+STDDiff = std(Difference);
+
+if Graphic == 1
+    plot(MeanEst,Difference,'ko')
+    xlabel 'Phase'
+    ylabel 'Difference'
+end
+end

### 2014-06-05 Matlab/Time_varying_sinewave.m
Corrected phase component

@@ -1,4 +1,4 @@
-function [TDSignal, TDPhase, Time, Freqs] = Time_varying_sinewave(CentralFreq, STDFreq, Order, Length, DT, Graphic)
+function [TDSignal, TDPhase, TDPhaseUnwrap, Time, Freqs] = Time_varying_sinewave(CentralFreq, STDFreq, Order, Length, DT, Graphic)
 %[TDSignal, TDPhase, Time, Freqs] = Time_varying_sinewave(CentralFreq, STDFreq, Order, Length, DT, Graphic)
 %
 %%
@@ -8,12 +8,12 @@ TDSignal = [];
 TDPhase = [];
 for N = 1:Order
     Period = round(1/f(N)/DT);
+    AngFreq = (2*pi)/Period;
     TempTime = 0:Period-1;
     TempSignal=cos(TempTime/Period*2*pi);
     TDSignal = [TDSignal,TempSignal];
-    TempPhase = 0:2*pi/length(TempTime):pi;
-    TempPhase2 = -pi:2*pi/length(TempTime):0-2*pi/length(TempTime);
-    TDPhase = [TDPhase,TempPhase,TempPhase2];
+    TempPhase = AngFreq*TempTime;
+    TDPhase = [TDPhase,TempPhase];
 end
 if length(Time)<length(TDSignal)
     fprintf('The specified length was too short \nto accomodate the order and sampling frequency.\n Length was changed to %d\n',length(TDSignal))
@@ -23,18 +23,29 @@ else
        TDSignal = [TDSignal,TDSignal];
        TDPhase = [TDPhase,TDPhase];
     end
-    TDSignal = TDSignal(1:length(Time));
+    TDSignal = TDSignal(1:length(Time))';
     TDPhase = TDPhase(1:length(Time));
 end
 
+TDPhaseUnwrap = unwrap(TDPhase);
+Freqs = f;
+
 if Graphic
     figure(101); clf;
-    ax1=subplot(211);
-        plot(TDPhase)
-    ax2=subplot(212);
+    ax1=subplot(311);
         plot(TDSignal)
+            ylabel 'Amplitude'
+            axis tight
+    ax2=subplot(312);
+        plot(TDPhaseUnwrap)
+            ylabel 'Phase (rad)'
+            axis tight
+    ax3=subplot(313);
+        plot(Freqs,'k.')
[…]

### 2014-06-05 Matlab/hilbert_interp.m
added bandpass filter

@@ -1,4 +1,4 @@
-function [phh,phhu,phhw,w,wi] =  hilbert_interp(Signal,Dt,f1,f2,Graphic)
+function [TDPhase] =  hilbert_interp(Signal,Dt,f1,f2,Graphic)
 %% Hilbert Interp %%
 % function purpose is to use the hilbert transform of a signal and estimate
 % the instantaneous phase and frequency of the signal
@@ -9,11 +9,7 @@ function [phh,phhu,phhw,w,wi] =  hilbert_interp(Signal,Dt,f1,f2,Graphic)
 % f2 - upper bound for the frequency range of the oscillation of interest
 % Graphic - 1 for plots, 0 for no plots
 %%%%%%%%%% Outputs %%%%%%%%%%
-% phh - Instantaneous phase wrapped to 2pi
-% phhu - Instantaneous phase unwrapped
-% phhw - Instantaneous unwrapped phase rewrapped to Pi
-% w = Instantaneous frequency
-% wi = Instantaneous frequency with phase slipes interpolated
+% TDPhase - unwrapped instantaneous phase with phase slips interpolated
 
 Fs = 1/Dt;  % Sampling Frequency
 %FOR MYO
@@ -27,9 +23,9 @@ Signal_f = filtfilt(b,a,Signal); %bandpass filter the input signal
 
 xh = hilbert(Signal_f);
 phh = angle(xh);
-phhu = unwrap(phh);
+TDPhase = unwrap(phh);
 
-    w = diff(phhu).*(2*2/pi);
+    w = diff(TDPhase).*(2*2/pi);
     wi = w;
 %% find data points where inst. frequency is outside filter pass band, and interpolate across those points
 t = Dt:Dt:length(Signal_f)*Dt;

### 2014-06-05 Matlab/wavelet_interp.m
update

@@ -1,4 +1,4 @@
-function [TDPhase] =  wavelet_interp(TDSignal, DT, Graphic)
+function TDPhase =  wavelet_interp(TDSignal, DT, Graphic)
 %%
 Time = 0:length(TDSignal)-1;
 Time=Time.*DT;
@@ -16,19 +16,19 @@ Power = abs(WN).^2;
 if Graphic
     figure(1);clf;
     mesh(Time, Period, Power) 
-    view(45,90);
+    view(90,45);
     colormap(hot)
 end
-%%
+%
 Size = size(Power,2);
 Phase_max = zeros(Size,1);
 for k = 1:Size
     [~,TempPeriod] = max(Power(:,k));
     Phase_max(k) = angle(WN(TempPeriod,k));
 end
-Phase_max_u = unwrap(Phase_max)';
-size(Phase_max)
-TDPhase = wrapToPi(Phase_max_u)';
+TDPhase = unwrap(Phase_max)';
+% size(Phase_max)
+% TDPhase = wrapToPi(Phase_max_u)';
 if Graphic
    figure(2); clf
    plot(TDPhase);

### 2014-06-05 Manuscript/Phase_detectors_outline.tex
added some notes

--- 2014-05-23 Manuscript/Phase_detectors_outline.tex
@@
 \subsection*{Potential physiology journals}
-The paper should have this structure:\cite{muller_estimation_2003}
+
 \begin{itemize}
@@
 \item Journal of experimental physiology
-\item Journal of Applied Phyiology
-\item E-Life
 \end{itemize}
@@
 
-\subsection*{Time-averaged phase, or Frequency domain phase}
+\subsection*{Frequency domain phase}
 
@@
 \end{itemize}
+
+Homeostasis is maintained by numerous interacting physiological control systems.
+Physiological systems are responsible for controlling a given output variable in response to one or more input variables.
+For example Heart rate is controlled by the autonomic nervous system to maintain blood pressure.
+Nonlinear responses between input and output in physiological systems are ubiquitous.
+Furthermore there are inherent delays in the response of each system because of inter and intra cellular signalling events.
+These nonlinearities
 
@@
 	\begin{itemize}
-	\item [Phase lag between changes in blood pressure and changes in heart rate] \hfill \\
+	\item Phase lag between changes in blood pressure and changes in heart rate
+
 The oscillations of blood pressure and heart rate are often compared using cross-spectral analyses to quantify baroreflex function.
@@
 Therefore, the phase relationship between these two signals is an important outcome measure for cardiovascular testing.
+
 	\end{itemize}
@@
 		\begin{enumerate}
-		\item Time series of raw simulated data + added noise
-		\item Power spectrum of the data
+		\item Time series of raw simulated data
 		\item Time-domain phase 
@@
 
-	\subsection*{Tables}
-		\begin{enumerate}
-			\item Simulation
-			\begin{enumerate}
-			\item Noise conversation
-				\begin{itemize}
-					\item Add gaussian noise from snr=$\infty$ up to when it breaks down.
-					\item It breaks down when 0 is not in the 95\% confidence interval of Bland-Altman-style statistics.		
-				\end{itemize}
-			\item Chirp (Frequency from point A to point B)
-				\begin{itemize}
-					\item Specifically to talk about limits to the bandpass filtering needed for the Hilbert method.
-				\end{itemize}
-			\item Length of signal
-				\begin{itemize}
-					\item Shorten the signal until techniques breakdown.
-					\item Relative to frequency.
-				\end{itemize}		
-			\end{enumerate}
-			\item Physiological Data
-
-		\end{enumerate}
-
-\bibliographystyle{plain}
-\bibliography{OutlineBib}
-
 \end{document}

### 2014-08-18 Matlab/BlandAltman.m
changed the outputs to be mean and standard deviation

@@ -1,9 +1,12 @@
 
-function [Difference,MeanEst,MeanDiff,STDDiff] = BlandAltman(Sig1,Sig2,Graphic)
+function [Difference,MeanEst,MeanDiff,STDDiff] = BlandAltman(Sig1,Sig2,Graphic, FigNo)
 %%
-
-EstPhases = [Sig1; Sig2]';
-
+Size = size(Sig1);
+if Size(1)>Size(2)
+    EstPhases = [Sig1, Sig2];
+else
+    EstPhases = [Sig1; Sig2]';
+end
 MeanEst = mean(EstPhases,2);
 
 Difference = Sig1 - Sig2;
@@ -12,8 +15,12 @@ MeanDiff = mean(Difference);
 STDDiff = std(Difference);
 
 if Graphic == 1
-    plot(MeanEst,Difference,'ko')
-    xlabel 'Phase'
+    figure(FigNo); clf;
+    plot(MeanEst,Difference,'ko'); hold on;
+    plot([min(MeanEst) max(MeanEst)],[MeanDiff MeanDiff],'r-');
+    plot([min(MeanEst) max(MeanEst)],[MeanDiff+1.96*STDDiff MeanDiff+1.96*STDDiff],'r--');
+    plot([min(MeanEst) max(MeanEst)],[MeanDiff-1.96*STDDiff MeanDiff-1.96*STDDiff],'r--');
+    xlabel 'Mean'
     ylabel 'Difference'
 end
 end

### 2014-08-18 Matlab/Phase_detectors_compare_run.m
changed the noise level 'style' to be in decibels

@@ -12,8 +12,8 @@ function [Time,TDSignal,TDPhaseUnwrap,TDPhase_Hilb,TDPhase_Wave,...
 NoiseVec = linspace(SNRMin,SNRMax,NoiseSteps);
 
 GWNSignal = zeros([Length/DT+1,NoiseSteps]);
-for k = 1:NoiseSteps
-    GWNSignal(:,k) = awgn(TDSignal,NoiseVec(k),'measured','linear');
+for k = 1:length(NoiseVec)
+    GWNSignal(:,k) = awgn(TDSignal,NoiseVec(k),'measured');
 end
 
 % Estimate phase with hilbert transform

### 2014-08-18 Matlab/Phase_detectors_compare_run.m
Trying to fix Nick's directory

@@ -23,8 +23,8 @@ f2 = CentralFreq+(0.5*CentralFreq);
 
 TDPhase_Hilb =  hilbert_interp(TDSignal,DT,f1,f2,Graphic);
 
-GWNPhase_Hilb = zeros([Length/DT+1,NoiseSteps]);
-GWNWrappedPhase_Hilb = zeros([Length/DT+1,NoiseSteps]);
+GWNPhase_Hilb = zeros([Length/DT+1-39,NoiseSteps]);
+GWNWrappedPhase_Hilb = zeros([Length/DT+1-39,NoiseSteps]);
 for k = 1:NoiseSteps
     [GWNPhase_Hilb(:,k), GWNWrappedPhase_Hilb(:,k)] = hilbert_interp(GWNSignal(:,k),DT,f1,f2,Graphic);
 end

### 2014-08-18 Matlab/hilbert_interp.m

@@ -24,7 +24,8 @@ Signal_f = filtfilt(b,a,Signal); %bandpass filter the input signal
 xh = hilbert(Signal_f);
 phh = angle(xh);
 WrappedPhase = phh;
-TDPhase = unwrap(phh);
+WrappedPhase = WrappedPhase(20:end-20);%Cut off edges to minimize edge effect
+TDPhase = unwrap(phh(20:end-20));
 
     w = diff(TDPhase).*(2*2/pi);
     wi = w;
@@ -38,11 +39,12 @@ ti=t(2:end);
 tt=ti;
 tt(kk1)=[];
 wi(kk1)=[];
-wi=interp1(tt,wi,ti,'linear','extrap'); 
+wi=interp1(tt,wi,ti(20:end-20),'linear','extrap'); 
 %%
 phh4=phh(2:end);
 phh4(kk1)=[];
 phh4=interp1(tt,phh4,ti,'linear','extrap')';
+phh4 = phh4(20:end-20);%Cut off edges to minimize edge effects
 
 phhw = wrapToPi(phh4);
 

### 2014-08-18 Matlab/wavelet_interp.m

@@ -24,9 +24,10 @@ Size = size(Power,2);
 Phase_max = zeros(Size,1);
 for k = 1:Size
     [~,TempPeriod] = max(Power(:,k));
-    Phase_max(k) = angle(WN(TempPeriod,k));
+    Phase_max(k) = mean(angle(WN(max(TempPeriod-2,1):min(TempPeriod+2,end),k)));
 end
 WrappedPhase = Phase_max';
+Phase_max = Phase_max(20:end-20);%Cut off edges to minimize edge effects
 TDPhase = unwrap(Phase_max)';
 % size(Phase_max)
 % TDPhase = wrapToPi(Phase_max_u)';

### 2014-08-18 Manuscript/Hilbert_transform.tex

\documentclass{article}
\usepackage{fullpage}
\usepackage{enumerate}
\usepackage{amsmath}
\begin{document}
\title{Hilbert transform as a phase detector}
\author{}
\date{}
\maketitle
The Hilbert transform is a simple linear operation that allows the detection of instantaneous phase from time series data. The overall process of extracting instantaneous phase is a three-step process: \begin{enumerate}
	\item Hilbert transform time-series data 
	\item Take the absolute value of the complex-valued result of the Hilbert transform
	\item Perform the inverse tangent on the real and imaginary portions of the result to get polar coordinates, which are equal to the phase of the original data
\end{enumerate}	
Here, we will explain why the Hilbert transform allows phase extraction from data. The non-mathematical reader can skip this section and continue in the next paragraph. We used the analytic signal concept introduced by Gabor in 1946. The first step in this process is to form a complex-valued signal from the scalar time series $s\left(t\right)$ by the following equation $$ \zeta\left(t\right)=s\left(t\right)+\tilde{s}\left(t\right)=A\left(t\right)e^{\phi t}$$ where $\tilde{s}\left(t\right)$ is the Hilbert transform of the original series $s\left(t\right)$.

The Hilbert transform is a linear operation that transforms a time-domain signal into another time-domain signal. The Hilbert transform acts as a filter whose magnitude characteristics are
$$ |H(f)| = 1 \mbox{ for all f }$$
and whose phase characteristics are
\[ H(f)=
	\begin{cases}
		\frac{-\pi}{2} & f > 0\\
		\frac{\pi}{2} & f < 0
	\end{cases}
\]

meaning that is essence the Hilbert transform causes a phase shift

Apparently this boils down to the convolution of a time series with $\frac{1}{\pi t}$ as such
$$\phi (t) = s(t) \ast \frac{1}{\pi t}$$

\textit{It is still not intuitively obvious why this gives you the phase of a signal, but all the engineering papers seem to take this for granted.}
\end{document}

### 2014-08-18 Matlab/BlandAltman.m
Trying to fix git issues

@@ -1,0 +1,26 @@
+
+function [Difference,MeanEst,MeanDiff,STDDiff] = BlandAltman(Sig1,Sig2,Graphic, FigNo)
+%%
+Size = size(Sig1);
+if Size(1)>Size(2)
+    EstPhases = [Sig1, Sig2];
+else
+    EstPhases = [Sig1; Sig2]';
+end
+MeanEst = mean(EstPhases,2);
+
+Difference = Sig1 - Sig2;
+
+MeanDiff = mean(Difference);
+STDDiff = std(Difference);
+
+if Graphic == 1
+    figure(FigNo); clf;
+    plot(MeanEst,Difference,'ko'); hold on;
+    plot([min(MeanEst) max(MeanEst)],[MeanDiff MeanDiff],'r-');
+    plot([min(MeanEst) max(MeanEst)],[MeanDiff+1.96*STDDiff MeanDiff+1.96*STDDiff],'r--');
+    plot([min(MeanEst) max(MeanEst)],[MeanDiff-1.96*STDDiff MeanDiff-1.96*STDDiff],'r--');
+    xlabel 'Mean'
+    ylabel 'Difference'
+end
+end

### 2014-08-18 Matlab/DetectionRatio.m

@@ -1,0 +1,34 @@
+function DetectionRatio = DetectionRatio(Signal,FS,FSigLow,FSigHigh,FNoiseLow,FNoiseHigh)
+%%%%%% Detection ratio determines an index of signal:noise ratio in raw data
+
+%%%%%%% Inputs %%%%%%%
+% Signal - time domain data signal
+% FSigLow - low end of frequency where the signal is likely to be
+% FSigHigh - high end of frequency where the signal is likely to be
+% FNoiseLow - low end of noise frequency range
+% FNoiseHigh - high end of noise frequency range
+
+%%%%%%% Outputs %%%%%%%
+% Detection ratio
+
+% find power spectrum using welch's method
+[PSD,f] = pwelch(Signal,[],[],512,FS);
+
+% find location in frequency range for signal and for noise
+Sigfreq1 = find(f<FSigLow,1,'last');
+Sigfreq2 = find(f>FSigHigh,1,'first');
+Noifreq1 = find(f<FNoiLow,1,'last');
+Noifreq2 = find(f>FNoiHigh,1,'first');
+% get max power within signal range
+Psig = max(PSD(Sigfreq1:Sigfreq2));
+% get mean power within noise range
+Pnoi = mean(PSD(Noifreq1:Noifreq2));
+% calculate standard deviation of noise range power
+SDnoi = std(PSD(Noifreq1:Noifreq2));
+% calculate DR
+DetectionRatio = 10*log10((Psig-Pnoi)/SDnoi);
+
+
+
+
+end

### 2014-08-18 Matlab/Generate_TIV_signal.m

@@ -1,0 +1,83 @@
+%%%%%%%%%%%%%%%% Generate a set of time-invariant waves with increasing %%%%%%%%%%%%
+%%%%%%%%%%%%%%%% uniform noise. Use Hilbert and wavelet methods to isolate %%%%%%%%%
+%%%%%%%%%%%%%%%% the instantaneous frequency and phase of each wave %%%%%%%%%%%%%%%%
+
+F1 = 1;
+F2 = 2;
+a = 1;
+Fs = 8;
+dur = 30;
+shift = 0;
+Period1 = 1/F1;
+Period2 = 1/F2;
+dt = 1/Fs;                   % seconds per sample
+t = (0:dt:dur-dt)';
+
+nRangeMin = 0;
+nRangeMax = 1;
+nSamples = 4;
+gauss = 0;
+
+
+x1 = makesine(F1,a,Fs,dur/2,shift);
+x2 = makesine(F2,a,Fs,dur/2,shift);
+xs = [x1; x2];
+
+[x,noi] = addWhiteNoise(xs,nRangeMin,nRangeMax,nSamples,gauss);
+
+siz = size(x,1);
+freq1 = ones(siz/2,1).*F1;
+freq2 = ones(siz/2,1).*F2;
+freq = [freq1; freq2];
+
+phase_step1 = (2*pi)/(Period1/dt);
+phase_step2 = (2*pi)/(Period2/dt);
+
+pht1 = 0:phase_step1:(length(t)/2)*phase_step1-phase_step1;
+pht2 = (0:phase_step2:(length(t)/2)*phase_step2-phase_step2)+max(pht1);
+pht = [pht1 pht2];
+
+ang_freq = Fs*mean(diff(pht));
+
+for k = 1:nSamples
+[phh(:,k),phhu(:,k),phhw(:,k),w(:,k),wi(:,k)] =  hilbert_interp(x(:,k));
+end
+
+for k = 1:nSamples
+[~,~,~,~,phase_max_u(k,:),phase_max_w(k,:),wi_w(k,:)] =  wavelet_interp(x(:,k));
+end
+%
+wd = 0.4;
+h = 0.4;
+s = 0.04;
+l1 = 0.08;
+l2 = l1+wd+s;
+b1 = 0.08;
+b2 = b1+h+s;
+
+subplot('Position',[l1,b2,wd,h])
+plot(phhu)
+ylabel 'Phase'
+title Hilbert
+ylim([-50 400])
+set(gca,'XTickLabel','')
[…]

### 2014-08-18 Matlab/Generate_TV_signal.m

@@ -1,0 +1,39 @@
+%%% generate TV signal %%%
+
+f1 = 0.1; %low frequency
+f2 = 0.3; % high frequency
+len = 500; % duration in seconds
+AM = 1; % amplitude modulation 
+FM = 0; % frequency modulation
+noi = 0; % add GWN
+t = 1:len;
+
+[x]=test_sig_AMFM(f1,f2,len,AM,FM,noi);
+
+
+ 
+% res=256; %frequency resolution
+dt=1; %sampling rate
+dj=0.0625; %wavelet interval
+J1=127; %total # of scales
+pad=1; %zero-pad signals
+s0=2*dt; %set initial scale
+mother='Morlet'; %wavelet shape
+param=6; %initial wavelet order
+% az = 63;
+% el = 46;
+az = 45;
+el = 90;
+
+%computes the wavelets
+[WN1,~,scales] = wavelet(x,dt,pad,dj,s0,J1,mother,param);
+freq=1./(1.033*scales);
+power = abs(WN1).^2;
+
+mesh(t,freq,power)
+view(az,el)
+colormap(hot)
+xlabel('Time (s)')
+ylabel('Frequency (Hz)')
+zlabel('Power (Units^2/Hz)')
+

### 2014-08-18 Matlab/MkSgateData2.m

@@ -1,0 +1,47 @@
+function [ SgateData, Time, Freqs ] = MkSgateData2( Length, dt,...
+    Freq1, Power1, STD1, Phase1, Freq2, Power2, STD2, Phase2)
+%[ SgateData ] = MkSgateData2( Length, dt, Freq1, Power1, STD1, Phase1, Freq2, Power2, STD2, Phase2)
+%
+%SgateData creates a time series from 2 oscillators of frequencies Freq1
+%and Freq2, Phase1 and Phase2, with some frequency noise related to STD1 and STD2
+%
+%Length: length of the time series in seconds
+%dt: sampling rate in seconds
+%%
+Time = (0:dt:Length);
+Freqs = (Time(1:ceil(length(Time)/2))./(length(Time)))./dt^2;
+Order = 1000;
+%%
+Oscillator1= zeros(size(Time));
+Fuzz = STD1*randn(Order,1);
+Fuzz2 = STD1*randn(Order,1)/5;
+Fuzz=Fuzz-mean(Fuzz);
+Fuzz2=fliplr(Fuzz2)-mean(fliplr(Fuzz2));
+for N=1:Order
+    N
+    [~, Mindex] = min(abs(Freqs-(Freq1+Fuzz(N))));
+    FuzzyFreq = Freqs(Mindex);
+%    FuzzyFreq = (Freq1+Fuzz(N));
+    FuzzyPhase = Phase1+Fuzz2(N);
+    FuzzyPower = Power1*(max(abs(Fuzz))-abs(Fuzz(N)))/...
+        sum(max(abs(Fuzz))-abs(Fuzz));
+%   FuzzyPower=1;
+    Oscillator1=Oscillator1+ awgn(FuzzyPower*...
+        cos((Time)*(2*pi)*(FuzzyFreq)-FuzzyPhase),4,'measured');
+end
+%%
+Oscillator2= zeros(size(Time));
+Fuzz = STD2*randn(Order,1);
+for N=1:Order
+    FuzzyFreq = Freq2 + Fuzz(N);
+    FuzzyPhase = Phase2 + Fuzz(N);
+    FuzzyPower = Power2*(max(abs(Fuzz))-abs(Fuzz(N)))/...
+        sum(max(abs(Fuzz))-abs(Fuzz));
+    Oscillator2=Oscillator2+ FuzzyPower*...
+        cos((Time)*(2*pi)*(FuzzyFreq)-FuzzyPhase);
+end
+%%
[…]

### 2014-08-18 Matlab/Phase_Detectors.m

@@ -1,0 +1,1 @@
+%%%%%%%%%% matlab %%%%%%%%%%

### 2014-08-18 Matlab/Phase_detectors_compare_run.m

@@ -1,0 +1,55 @@
+function [Time,TDSignal,TDPhaseUnwrap,TDPhase_Hilb,TDPhase_Wave,...
+    Difference_Hilb1,MeanEst_Hilb1,MeanDiff_Hilb1,STDDiff_Hilb1,...
+    Difference_Wave1,MeanEst_Wave1,MeanDiff_Wave1,STDDiff_Wave1,...
+    Difference_Hilb,MeanEst_Hilb,MeanDiff_Hilb,STDDiff_Hilb,...
+    Difference_Wave,MeanEst_Wave,MeanDiff_Wave,STDDiff_Wave] = ...
+    Phase_detectors_compare_run(CentralFreq,STDFreq,Order,Length,DT,...
+    Graphic,SNRMin,SNRMax,NoiseSteps)
+%%
+[TDSignal, TDPhase , TDPhaseUnwrap, Time, ~] = Time_varying_sinewave(CentralFreq, STDFreq, Order, Length, DT, Graphic);
+
+% Add noise to test signal
+NoiseVec = linspace(SNRMin,SNRMax,NoiseSteps);
+
+GWNSignal = zeros([Length/DT+1,NoiseSteps]);
+for k = 1:length(NoiseVec)
+    GWNSignal(:,k) = awgn(TDSignal,NoiseVec(k),'measured');
+end
+
+% Estimate phase with hilbert transform
+f1 = CentralFreq-(0.5*CentralFreq);
+f2 = CentralFreq+(0.5*CentralFreq);
+
+
+TDPhase_Hilb =  hilbert_interp(TDSignal,DT,f1,f2,Graphic);
+
+GWNPhase_Hilb = zeros([Length/DT+1-39,NoiseSteps]);
+GWNWrappedPhase_Hilb = zeros([Length/DT+1-39,NoiseSteps]);
+for k = 1:NoiseSteps
+    [GWNPhase_Hilb(:,k), GWNWrappedPhase_Hilb(:,k)] = hilbert_interp(GWNSignal(:,k),DT,f1,f2,Graphic);
+end
+% Estimate phase with wavelet transform
+
+TDPhase_Wave =  wavelet_interp(TDSignal, DT, Graphic);
+
+GWNPhase_Wave = zeros([Length/DT+1,NoiseSteps]);
+GWNWrappedPhase_Wave = zeros([Length/DT+1,NoiseSteps]);
+for k = 1:NoiseSteps
[…]

### 2014-08-18 Matlab/Phase_detectors_compare_trials.m

@@ -1,0 +1,151 @@
+%%%%%%%%%%%%%% Phase detector simulation %%%%%%%%%%%%%%
+% This script calls multiple other functions in order to make a series of sine waves
+% with multiple frequencies and increasing levels of noise. The phase of each wave
+% is then esimated with Wavelet and Hilbert transforms and their agreement wih the
+% true phase of the original noise-free wave is shown with a Bland-Altman plot. Then
+% the average agreement is shown at each noise level over multiple repetitions.
+
+%%%%%%%%%%%% Inputs %%%%%%%%%%%% 
+% CentralFreq - the central frequency of the sine wave
+% STDFreq - standard deviation of the frequecy over time
+% Order - the number of frequencies used in the wave
+% Length - Duration of the wave in seconds
+% DT - Time step of the wave, equal to 1/sample frequency
+% Graphic - 1 for plots, 0 for no plots
+% SNRMin - minimum signal to noise ratio in dB
+% SNRMax - maximum signal to noise ratio
+% NoiseSteps - number of individual signal to noise ratios to test
+% Trials - Number of times to repeat the analysis
+
+%%%%%%%%%%%% Outputs %%%%%%%%%%%% 
+
+% TDSignal - Original sine wave with no noise
+% TDPhaseUnwrap - True phase of TDSignal
+% TDPhase_Hilb - Estimated phase with Hilbert method
+% TDPhase_Wave - Estimated phase with Wavelet method
+% Difference_Hilb1 - Difference between true phase and Hilbert estimated phase without noise
+% MeanEst_Hilb1 - Mean of True phase and Hilbert estimated phase
+% Difference_Wave1 - Difference between true phase and Wavelet estimated phase without noise
+% MeanEst_Wave1 - Mean of True phase and Wavelet estimated phase
+%%
+tic
+
+CentralFreq = 0.2;
+STDFreq = CentralFreq*0.1;
+Order = 12;
+Length = 120;
[…]

### 2014-08-18 Matlab/Time_varying_sinewave.m

@@ -1,0 +1,52 @@
+function [TDSignal, TDPhase, TDPhaseUnwrap, Time, Freqs] = Time_varying_sinewave(CentralFreq, STDFreq, Order, Length, DT, Graphic)
+%[TDSignal, TDPhase, Time, Freqs] = Time_varying_sinewave(CentralFreq, STDFreq, Order, Length, DT, Graphic)
+%
+%%
+Time = 0:DT:Length;
+f = STDFreq*randn(Order,1) + CentralFreq;
+TDSignal = [];
+TDPhase = [];
+for N = 1:Order
+    Period = round(1/f(N)/DT);
+    AngFreq = (2*pi)/Period;
+    TempTime = 0:Period-1;
+    TempSignal=cos(TempTime/Period*2*pi);
+    TDSignal = [TDSignal,TempSignal];
+    TempPhase = AngFreq*TempTime;
+    TDPhase = [TDPhase,TempPhase];
+end
+if length(Time)<length(TDSignal)
+    fprintf('The specified length was too short \nto accomodate the order and sampling frequency.\n Length was changed to %d\n',length(TDSignal))
+    Time = (0:length(TDSignal)-1);
+else
+    while length(Time)>length(TDSignal)
+       TDSignal = [TDSignal,TDSignal];
+       TDPhase = [TDPhase,TDPhase];
+    end
+    TDSignal = TDSignal(1:length(Time))';
+    TDPhase = TDPhase(1:length(Time));
+end
+
+TDPhase = wrapToPi(TDPhase);
+TDPhaseUnwrap = unwrap(TDPhase);
+Freqs = f;
+
+if Graphic
+    figure(101); clf;
+    ax1=subplot(311);
+        plot(TDSignal)
+            ylabel 'Amplitude'
+            axis tight
+    ax2=subplot(312);
+        plot(TDPhaseUnwrap)
+            ylabel 'Phase (rad)'
+            axis tight
+    ax3=subplot(313);
+        plot(Freqs,'k.')
+        line([0 length(Freqs)],[CentralFreq CentralFreq],'color','k','LineStyle','--')
+            ylabel 'Frequency (Hz)'
+  
+    linkaxes([ax1 ax2],'x')
+end
+
+end

### 2014-08-18 Matlab/Wavelet_phase_estimate.m

@@ -1,0 +1,45 @@
+
+
+F1 = 1;
+F2 = 2;
+a = 1;
+Fs = 8;
+dur = 30;
+shift = 0;
+Period1 = 1/F1;
+Period2 = 1/F2;
+dt = 1/Fs;                   % seconds per sample
+t = (0:dt:dur-dt)';
+
+x1 = makesine(F1,a,Fs,dur/2,shift);
+x2 = makesine(F2,a,Fs,dur/2,shift);
+xs = [x1; x2];
+
+res=256; %frequency resolution
+dt=1; %sampling rate
+dj=0.0625; %wavelet interval
+J1=127; %total # of scales
+pad=1; %zero-pad signals
+s0=2*dt; %set initial scale
+mother='Morlet'; %wavelet shape
+param=6; %initial wavelet order
+
+%computes the wavelets
+[WN1,~,scales] = wavelet(xs,dt,pad,dj,s0,J1,mother,param);
+freq=1./(1.033*scales);
+power = abs(WN1).^2;
+%%
+siz = size(power,2);
+
+for k = 1:siz
+    [~,idx(k)] = max(power(:,k));
+    phase_max(k) = angle(WN1(idx(k),k));
+end
+phase_max_u = unwrap(phase_max);
+phase_max_w = wrapToPi(phase_max_u);
+
+plot(phase_max_w)
+
+%%
+imagesc(t,freq,power)
+ylabel 'Frequency'

### 2014-08-18 Matlab/hilbert_interp.m

@@ -1,0 +1,71 @@
+function [TDPhase, WrappedPhase] =  hilbert_interp(Signal,Dt,f1,f2,Graphic)
+%% Hilbert Interp %%
+% function purpose is to use the hilbert transform of a signal and estimate
+% the instantaneous phase and frequency of the signal
+%%%%%%%%%% Inputs %%%%%%%%%%
+% Signal - the time domain signal to be analyzed
+% Dt - Time step for the signal i.e. 1/sample frequency
+% f1 - lower bound of the frequency range for the oscillation of interest
+% f2 - upper bound for the frequency range of the oscillation of interest
+% Graphic - 1 for plots, 0 for no plots
+%%%%%%%%%% Outputs %%%%%%%%%%
+% TDPhase - unwrapped instantaneous phase with phase slips interpolated
+
+Fs = 1/Dt;  % Sampling Frequency
+%FOR MYO
+N   = 6;    % Order
+% Construct an FDESIGN object and call its BUTTER method.
+h  = fdesign.bandpass('N,F3dB1,F3dB2', N, f1, f2, Fs);
+Hd = design(h, 'butter');
+[b,a]=sos2tf(Hd.sosMatrix,Hd.ScaleValues);
+
+Signal_f = filtfilt(b,a,Signal); %bandpass filter the input signal
+
+xh = hilbert(Signal_f);
+phh = angle(xh);
+WrappedPhase = phh;
+WrappedPhase = WrappedPhase(20:end-20);%Cut off edges to minimize edge effect
+TDPhase = unwrap(phh(20:end-20));
+
+    w = diff(TDPhase).*(2*2/pi);
+    wi = w;
+%% find data points where inst. frequency is outside filter pass band, and interpolate across those points
+t = Dt:Dt:length(Signal_f)*Dt;
+k1=find(wi<0);
+kk1=[k1;k1+1;k1-1];
+kk1(kk1<=0)=[];
+kk1(kk1>length(wi))=[];
+ti=t(2:end);
+tt=ti;
+tt(kk1)=[];
+wi(kk1)=[];
+wi=interp1(tt,wi,ti(20:end-20),'linear','extrap'); 
+%%
+phh4=phh(2:end);
+phh4(kk1)=[];
+phh4=interp1(tt,phh4,ti,'linear','extrap')';
[…]

### 2014-08-18 Matlab/makesine.m

@@ -1,0 +1,11 @@
+function x = makesine(F,a,Fs,dur,shift)
+% F1 = wave frequency (hz)
+% a = amplitude
+% Fs = sample frequency
+% dur = duration in seconds
+% shift = phase shift in radians
+                  % samples per second
+dt = 1/Fs;                   % seconds per sample
+t = (0:dt:dur-dt)';     % seconds
+x = a*cos(2*pi*F*(t+shift)); 
+end

### 2014-08-18 Matlab/test_sig_AMFM.m

@@ -1,0 +1,83 @@
+function [x]=test_sig_AMFM(f1,f2,len,AM,FM,noi)
+%TEST SIGNAL FOR TGF AM/FM on MYO
+%AM = 1 to have amplitude modulation
+%FM = 1 to have frequency modulation
+%len = signal length
+%noi = 1 to add WGN
+%f1 = TGF Frequency
+%f2 = MYO Frequency
+%x = output signal
+%tfr = time-frequency representation
+
+t=1:len;
+
+%generate low frequency component
+phi1=-pi+2*pi*rand;
+LF=sin(2*pi*f1.*t+phi1);
+
+if AM ~= 1 && FM ~= 1
+    phi2=-pi+2*pi*rand;
+    HF=cos(2*pi*f2.*t+phi2);
+elseif AM == 1 && FM ~=1
+    %if AM but not FM
+    phi2=-pi+2*pi*rand;
+    HF=(1+0.75.*LF).*cos(2*pi*f2.*t+phi2);
+elseif AM ~= 1 && FM ==1
+    % if FM, no AM
+    mHF=cos(2*pi*f1.*t);
+    for n=1:length(t)
+        mm(n)=sum(mHF(1:n));
+    end
+    HF=cos(2*pi*f2.*t+2*pi*f1.*mm);
+elseif AM ==1 && FM == 1
+    % if AM and FM
+    mHF=cos(2*pi*f1.*t);
+    for n=1:length(t)
+        mm(n)=sum(mHF(1:n));
+    end
+    HF=(1+0.75.*LF).*cos(2*pi*f2.*t+2*pi*f1.*mm);
+end
+
+x=LF+HF;
+
+%GENERATE IDEAL TFR OF TEST SIGNAL
+% tfr=zeros(256,500);
+% test=hilbert(HF');
+% test=instfreq(test);
+% for n=1:length(t)-2
+%     k1=find(f<test(n));
+%     k2=find(f>test(n));
+%     kt=abs(test(n)-f(k1(end)));
+%     ktt=abs(test(n)-f(k2(1)));
+%     if kt<ktt
+%         fcurr_ind(n)=k1(end);
+%     else
+%         fcurr_ind(n)=k2(1);
+%     end
+% end
+% 
+% for n=2:length(t)-1
+%     tfr(fcurr_ind(n-1),n)=1+0.5.*LF(n);
+% end
+% 
+% test=hilbert(LF');
+% test=instfreq(test);
[…]

### 2014-08-18 Matlab/wavelet_interp.m

@@ -1,0 +1,39 @@
+function [TDPhase, WrappedPhase] =  wavelet_interp(TDSignal, DT, Graphic)
+%%
+Time = 0:length(TDSignal)-1;
+Time=Time.*DT;
+dj=0.04; %wavelet interval
+J1=127; %total # of scales
+pad=1; %zero-pad signals
+s0=0.5; %set initial scale
+mother='Morlet'; %wavelet shape
+param=6; %initial wavelet order
+
+%computes the wavelets
+[WN,Period,~] = wavelet(TDSignal,DT,pad,dj,s0,J1,mother,param);
+Power = abs(WN).^2;
+%Freqs=1./(1.033.*Scale);
+if Graphic
+    figure(1);clf;
+    mesh(Time, Period, Power) 
+    view(90,45);
+    colormap(hot)
+end
+%
+Size = size(Power,2);
+Phase_max = zeros(Size,1);
+for k = 1:Size
+    [~,TempPeriod] = max(Power(:,k));
+    Phase_max(k) = mean(angle(WN(max(TempPeriod-2,1):min(TempPeriod+2,end),k)));
+end
+WrappedPhase = Phase_max';
+Phase_max = Phase_max(20:end-20);%Cut off edges to minimize edge effects
+TDPhase = unwrap(Phase_max)';
+% size(Phase_max)
+% TDPhase = wrapToPi(Phase_max_u)';
+if Graphic
+   figure(2); clf
+   plot(TDPhase);
+end
+%wi = (diff(Phase_max_u).*2*2/pi)';
+end

### 2014-08-18 Matlab/Phase_Detectors_Generate_Figure1.m
Figure 1 for paper

@@ -1,0 +1,66 @@
+%%%% Phase detectors Figure 1
+
+% generate simulated data
+Phase_detectors_compare_trials
+%%
+SNRMin = -100;
+SNRMax = 50;
+NoiseSteps = 151;
+
+NoiseVec = linspace(SNRMin,SNRMax,NoiseSteps);
+
+GWNSignal = zeros([Length/DT+1,NoiseSteps]);
+for k = 1:NoiseSteps
+    GWNSignal(:,k) = awgn(TDSignal,NoiseVec(k),'measured');
+end
+
+SNRValue = -20; %The SNR to be plotted as the "noisy" signal (in dB)
+SNRLoc = find(NoiseVec==SNRValue);
+
+%% 
+Filt = 1;
+f1 = CentralFreq-0.5*CentralFreq;
+f2 = CentralFreq+0.5*CentralFreq;
+
+NoisyPhase_Wave =  wavelet_interp(GWNSignal(:,SNRLoc), DT, Filt, f1, f2, Graphic);
+[NoisyPhase_Hilb,~] =  hilbert_interp(GWNSignal(:,SNRLoc),DT,Filt,f1,f2,Graphic);
+%% plot signals, phases
+w = 0.5;
+h = 0.26;
+s = 0.04;
+l = 0.25;
+
+b1 = 0.08;
+b2 = b1 + h + s;
+b3 = b2 + h + s;
+
+FontN = 'Arial';
+FontSz = 12;
+LGrey = [0.5 0.5 0.5];
+DGrey = [0.3 0.3 0.3];
+
+YMax = 1.1*max(GWNSignal(:,SNRLoc));
+YMin = 1.1*min(GWNSignal(:,SNRLoc));
+
+figure(1)
+
+subplot('Position',[l,b3,w,h])
+    plot(Time,TDSignal,'k-')
+        ylim([-1.2 1.2])
+        set(gca,'XTickLabel','')
+
+subplot('Position',[l,b2,w,h])
+    plot(Time,GWNSignal(:,SNRLoc),'k-')
+        ylim([YMin YMax])
+        set(gca,'XTickLabel','')
+
+subplot('Position',[l,b1,w,h])
+    plot(Time,TDPhaseUnwrap,'k-'); hold on
+    plot(Time,NoisyPhase_Hilb,'color',DGrey)
+    plot(Time,NoisyPhase_Wave,'color',LGrey)
+        legend('True','Hilbert','Wavelet','Location','NorthWest')
+
+
+
+
+

### 2014-08-18 Matlab/Phase_Detectors_Generate_Figure1.m
Update to wavelet

@@ -22,8 +22,8 @@ Filt = 1;
 f1 = CentralFreq-0.5*CentralFreq;
 f2 = CentralFreq+0.5*CentralFreq;
 
-NoisyPhase_Wave =  wavelet_interp(GWNSignal(:,SNRLoc), DT, Filt, f1, f2, Graphic);
-[NoisyPhase_Hilb,~] =  hilbert_interp(GWNSignal(:,SNRLoc),DT,Filt,f1,f2,Graphic);
+NoisyPhase_Wave =  wavelet_interp(GWNSignal(:,SNRLoc), DT, f1, f2, Graphic);
+[NoisyPhase_Hilb,~] =  hilbert_interp(GWNSignal(:,SNRLoc),DT,f1,f2,Graphic);
 %% plot signals, phases
 w = 0.5;
 h = 0.26;

### 2014-08-18 Matlab/wavelet_interp.m

@@ -1,4 +1,4 @@
-function [TDPhase, WrappedPhase] =  wavelet_interp(TDSignal, DT, Graphic)
+function [TDPhase, WrappedPhase] =  wavelet_interp(TDSignal, DT, f1, f2, Graphic)
 %%
 Time = 0:length(TDSignal)-1;
 Time=Time.*DT;
@@ -8,6 +8,16 @@ pad=1; %zero-pad signals
 s0=0.5; %set initial scale
 mother='Morlet'; %wavelet shape
 param=6; %initial wavelet order
+
+Fs = 1/DT;  % Sampling Frequency
+%FOR MYO
+N   = 6;    % Order
+% Construct an FDESIGN object and call its BUTTER method.
+h  = fdesign.bandpass('N,F3dB1,F3dB2', N, f1, f2, Fs);
+Hd = design(h, 'butter');
+[b,a]=sos2tf(Hd.sosMatrix,Hd.ScaleValues);
+
+TDSignal = filtfilt(b,a,TDSignal);
 
 %computes the wavelets
 [WN,Period,~] = wavelet(TDSignal,DT,pad,dj,s0,J1,mother,param);

### 2014-08-18 Matlab/Phase_detectors_compare_run.m
added Filt option to all trying to cut off edges to minimize edge effects

@@ -4,7 +4,7 @@ function [Time,TDSignal,TDPhaseUnwrap,TDPhase_Hilb,TDPhase_Wave,...
     Difference_Hilb,MeanEst_Hilb,MeanDiff_Hilb,STDDiff_Hilb,...
     Difference_Wave,MeanEst_Wave,MeanDiff_Wave,STDDiff_Wave] = ...
     Phase_detectors_compare_run(CentralFreq,STDFreq,Order,Length,DT,...
-    Graphic,SNRMin,SNRMax,NoiseSteps)
+    Graphic,SNRMin,SNRMax,NoiseSteps, Filt)
 %%
 [TDSignal, TDPhase , TDPhaseUnwrap, Time, ~] = Time_varying_sinewave(CentralFreq, STDFreq, Order, Length, DT, Graphic);
 
@@ -26,16 +26,16 @@ TDPhase_Hilb =  hilbert_interp(TDSignal,DT,f1,f2,Graphic);
 GWNPhase_Hilb = zeros([Length/DT+1-39,NoiseSteps]);
 GWNWrappedPhase_Hilb = zeros([Length/DT+1-39,NoiseSteps]);
 for k = 1:NoiseSteps
-    [GWNPhase_Hilb(:,k), GWNWrappedPhase_Hilb(:,k)] = hilbert_interp(GWNSignal(:,k),DT,f1,f2,Graphic);
+    [GWNPhase_Hilb(:,k), GWNWrappedPhase_Hilb(:,k)] = hilbert_interp(GWNSignal(:,k),DT,Filt, f1,f2,Graphic);
 end
 % Estimate phase with wavelet transform
 
 TDPhase_Wave =  wavelet_interp(TDSignal, DT, Graphic);
 
-GWNPhase_Wave = zeros([Length/DT+1,NoiseSteps]);
-GWNWrappedPhase_Wave = zeros([Length/DT+1,NoiseSteps]);
+GWNPhase_Wave = zeros([Length/DT+1-39,NoiseSteps]);
+GWNWrappedPhase_Wave = zeros([Length/DT+1-39,NoiseSteps]);
 for k = 1:NoiseSteps
-    [GWNPhase_Wave(:,k), GWNWrappedPhase_Wave(:,k)] = wavelet_interp(GWNSignal(:,k), DT, Graphic);
[…]

### 2014-08-18 Matlab/Phase_detectors_compare_trials.m

@@ -53,6 +53,7 @@ MeanDiff_Hilb = zeros([Trials,NoiseSteps]);
 STDDiff_Hilb = zeros([Trials,NoiseSteps]);
 MeanDiff_Wave = zeros([Trials,NoiseSteps]);
 STDDiff_Wave = zeros([Trials,NoiseSteps]);
+Filt = 1;
 for k = 1:Trials
     
     [Time,TDSignal,TDPhaseUnwrap,TDPhase_Hilb,TDPhase_Wave,Difference_Hilb1,...
@@ -61,7 +62,7 @@ for k = 1:Trials
         MeanEst_Hilb,MeanDiff_Hilb(k,:),STDDiff_Hilb(k,:),...
         Difference_Wave,MeanEst_Wave,MeanDiff_Wave(k,:),STDDiff_Wave(k,:)] = ...
         Phase_detectors_compare_run(CentralFreq,STDFreq,Order,Length,...
-        DT,Graphic,SNRMin,SNRMax,NoiseSteps);
+        DT,Graphic,SNRMin,SNRMax,NoiseSteps, Filt);
 end
 
 toc

### 2014-08-18 Matlab/hilbert_interp.m

@@ -1,4 +1,4 @@
-function [TDPhase, WrappedPhase] =  hilbert_interp(Signal,Dt,f1,f2,Graphic)
+function [TDPhase, WrappedPhase] =  hilbert_interp(Signal_f,Dt,Filt, f1,f2,Graphic)
 %% Hilbert Interp %%
 % function purpose is to use the hilbert transform of a signal and estimate
 % the instantaneous phase and frequency of the signal
@@ -15,11 +15,14 @@ Fs = 1/Dt;  % Sampling Frequency
 %FOR MYO
 N   = 6;    % Order
 % Construct an FDESIGN object and call its BUTTER method.
+f1
+f2
 h  = fdesign.bandpass('N,F3dB1,F3dB2', N, f1, f2, Fs);
 Hd = design(h, 'butter');
 [b,a]=sos2tf(Hd.sosMatrix,Hd.ScaleValues);
-
-Signal_f = filtfilt(b,a,Signal); %bandpass filter the input signal
+if Filt
+    Signal_f = filtfilt(b,a,Signal_f); %bandpass filter the input signal
+end
 
 xh = hilbert(Signal_f);
 phh = angle(xh);
@@ -30,18 +33,22 @@ TDPhase = unwrap(phh(20:end-20));
     w = diff(TDPhase).*(2*2/pi);
     wi = w;
 %% find data points where inst. frequency is outside filter pass band, and interpolate across those points
-t = Dt:Dt:length(Signal_f)*Dt;
-k1=find(wi<0);
-kk1=[k1;k1+1;k1-1];
-kk1(kk1<=0)=[];
-kk1(kk1>length(wi))=[];
-ti=t(2:end);
-tt=ti;
-tt(kk1)=[];
-wi(kk1)=[];
-wi=interp1(tt,wi,ti(20:end-20),'linear','extrap'); 
+ t = Dt:Dt:length(Signal_f)*Dt;
+ k1=find(wi<0);
+ kk1=[k1;k1+1;k1-1];
+ kk1(kk1<=0)=[];
+ kk1(kk1>length(wi))=[];
+ ti=t(2:end);
+ ti = ti(20:end-20);
+ tt=ti;
+ tt(kk1)=[];
+% wi(kk1)=[];
+% length(tt)
+% length(wi)
+% length(ti)
+% wi=interp1(tt,wi,ti,'linear','extrap'); 
 %%
-phh4=phh(2:end);
[…]

### 2014-08-18 Matlab/wavelet_interp.m

@@ -17,7 +17,10 @@ h  = fdesign.bandpass('N,F3dB1,F3dB2', N, f1, f2, Fs);
 Hd = design(h, 'butter');
 [b,a]=sos2tf(Hd.sosMatrix,Hd.ScaleValues);
 
-TDSignal = filtfilt(b,a,TDSignal);
+if Filt
+    TDSignal = filtfilt(b,a,TDSignal); %bandpass filter the input signal
+end
+
 
 %computes the wavelets
 [WN,Period,~] = wavelet(TDSignal,DT,pad,dj,s0,J1,mother,param);

### 2014-08-18 Matlab/Phase_detectors_compare_run.m
added filtering option done cutting out 30 units off the edges for phase graphs

@@ -21,19 +21,19 @@ f1 = CentralFreq-(0.5*CentralFreq);
 f2 = CentralFreq+(0.5*CentralFreq);
 
 
-TDPhase_Hilb =  hilbert_interp(TDSignal,DT,f1,f2,Graphic);
+TDPhase_Hilb =  hilbert_interp(TDSignal,DT,Filt,f1,f2,Graphic);
 
-GWNPhase_Hilb = zeros([Length/DT+1-39,NoiseSteps]);
-GWNWrappedPhase_Hilb = zeros([Length/DT+1-39,NoiseSteps]);
+GWNPhase_Hilb = zeros([Length/DT+1-59,NoiseSteps]);
+GWNWrappedPhase_Hilb = zeros([Length/DT+1-59,NoiseSteps]);
 for k = 1:NoiseSteps
     [GWNPhase_Hilb(:,k), GWNWrappedPhase_Hilb(:,k)] = hilbert_interp(GWNSignal(:,k),DT,Filt, f1,f2,Graphic);
 end
 % Estimate phase with wavelet transform
 
-TDPhase_Wave =  wavelet_interp(TDSignal, DT, Graphic);
+TDPhase_Wave =  wavelet_interp(TDSignal, DT,Filt, f1, f2, Graphic);
 
-GWNPhase_Wave = zeros([Length/DT+1-39,NoiseSteps]);
-GWNWrappedPhase_Wave = zeros([Length/DT+1-39,NoiseSteps]);
+GWNPhase_Wave = zeros([Length/DT+1-59,NoiseSteps]);
+GWNWrappedPhase_Wave = zeros([Length/DT+1-59,NoiseSteps]);
 for k = 1:NoiseSteps
     [GWNPhase_Wave(:,k), GWNWrappedPhase_Wave(:,k)] = wavelet_interp(GWNSignal(:,k), DT, Filt, f1, f2, Graphic);
 end
@@ -41,12 +41,12 @@ end
 % Determine agreement between each estimate and the true phase (Bland-Altman)
 GraphicBA = 0;
 % for noise free signals
-[Difference_Hilb1,MeanEst_Hilb1,MeanDiff_Hilb1,STDDiff_Hilb1] = BlandAltman(TDPhaseUnwrap,TDPhase_Hilb',GraphicBA);
[…]

### 2014-08-18 Matlab/Phase_detectors_compare_trials.m

@@ -89,8 +89,9 @@ ylim([ymin ymax])
 text(((xmax-xmin)/2),-1.4,'Time (s)','HorizontalAlignment','center')
 text(0,-6,'Ampltidude','HorizontalAlignment','center','Rotation',90)
 %% Plot True, Hilbert and Wavelet Phase
+Time = Time(30:end-30);
 figure(2); clf;
-plot(Time,TDPhaseUnwrap,'k-',Time,unwrap(TDPhase_Hilb),'bo',Time,TDPhase_Wave,'ro')
+plot(Time,TDPhaseUnwrap(30:end-30),'k-',Time,unwrap(TDPhase_Hilb),'bo',Time,TDPhase_Wave,'ro')
 xlim([0 100])
 xlabel 'Time (s)'
 ylabel 'Phase (rad)'

### 2014-08-18 Matlab/hilbert_interp.m

@@ -15,8 +15,6 @@ Fs = 1/Dt;  % Sampling Frequency
 %FOR MYO
 N   = 6;    % Order
 % Construct an FDESIGN object and call its BUTTER method.
-f1
-f2
 h  = fdesign.bandpass('N,F3dB1,F3dB2', N, f1, f2, Fs);
 Hd = design(h, 'butter');
 [b,a]=sos2tf(Hd.sosMatrix,Hd.ScaleValues);
@@ -27,8 +25,8 @@ end
 xh = hilbert(Signal_f);
 phh = angle(xh);
 WrappedPhase = phh;
-WrappedPhase = WrappedPhase(20:end-20);%Cut off edges to minimize edge effect
-TDPhase = unwrap(phh(20:end-20));
+WrappedPhase = WrappedPhase(30:end-30);%Cut off edges to minimize edge effect
+TDPhase = unwrap(phh(30:end-30))+2*pi;
 
     w = diff(TDPhase).*(2*2/pi);
     wi = w;
@@ -39,7 +37,7 @@ TDPhase = unwrap(phh(20:end-20));
  kk1(kk1<=0)=[];
  kk1(kk1>length(wi))=[];
  ti=t(2:end);
- ti = ti(20:end-20);
+ ti = ti(30:end-30);
  tt=ti;
  tt(kk1)=[];
 % wi(kk1)=[];
@@ -51,7 +49,7 @@ TDPhase = unwrap(phh(20:end-20));
 phh4=WrappedPhase(2:end);
 phh4(kk1)=[];
 phh4=interp1(tt,phh4,ti,'linear','extrap')';
-phh4 = phh4(20:end-20);%Cut off edges to minimize edge effects
+phh4 = phh4(30:end-30);%Cut off edges to minimize edge effects
 
 phhw = wrapToPi(phh4);
 

### 2014-08-18 Matlab/Phase_Detectors_Generate_Figure1.m
Figure 1 Complete

@@ -21,9 +21,9 @@ SNRLoc = find(NoiseVec==SNRValue);
 Filt = 1;
 f1 = CentralFreq-0.5*CentralFreq;
 f2 = CentralFreq+0.5*CentralFreq;
-
-NoisyPhase_Wave =  wavelet_interp(GWNSignal(:,SNRLoc), DT, f1, f2, Graphic);
-[NoisyPhase_Hilb,~] =  hilbert_interp(GWNSignal(:,SNRLoc),DT,f1,f2,Graphic);
+Graphic = 0;
+NoisyPhase_Wave =  wavelet_interp(GWNSignal(:,SNRLoc), DT, Filt, f1, f2, Graphic);
+[NoisyPhase_Hilb,~] =  hilbert_interp(GWNSignal(:,SNRLoc), DT, Filt, f1, f2, Graphic);
 %% plot signals, phases
 w = 0.5;
 h = 0.26;
@@ -36,31 +36,43 @@ b3 = b2 + h + s;
 
 FontN = 'Arial';
 FontSz = 12;
-LGrey = [0.5 0.5 0.5];
+LGrey = [0.7 0.7 0.7];
 DGrey = [0.3 0.3 0.3];
 
 YMax = 1.1*max(GWNSignal(:,SNRLoc));
 YMin = 1.1*min(GWNSignal(:,SNRLoc));
 
-figure(1)
+figure(1); clf
 
 subplot('Position',[l,b3,w,h])
-    plot(Time,TDSignal,'k-')
-        ylim([-1.2 1.2])
+    plot(Time,TDSignal(30:end-30),'k-')
+        ylim([-1.3 1.3])
         set(gca,'XTickLabel','')
+        box off
+        text(-15,0,'Amplitude','FontName',FontN,'FontSize',FontSz,'HorizontalAlignment','Center','Rotation',90)
+        text(-20,1.3,'A','FontName',FontN,'FontSize',FontSz+4,'FontWeight','Bold','HorizontalAlignment','Center','Rotation',0)
 
+        
 subplot('Position',[l,b2,w,h])
-    plot(Time,GWNSignal(:,SNRLoc),'k-')
+    plot(Time,GWNSignal(30:end-30,SNRLoc),'k-')
         ylim([YMin YMax])
         set(gca,'XTickLabel','')
+        box off
+        text(-15,0,'Amplitude','FontName',FontN,'FontSize',FontSz,'HorizontalAlignment','Center','Rotation',90)
[…]

### 2014-08-18 Matlab/wavelet_interp.m

@@ -37,11 +37,11 @@ Size = size(Power,2);
 Phase_max = zeros(Size,1);
 for k = 1:Size
     [~,TempPeriod] = max(Power(:,k));
-    Phase_max(k) = mean(angle(WN(max(TempPeriod-2,1):min(TempPeriod+2,end),k)));
+    Phase_max(k) = angle(WN(TempPeriod,k));
 end
-Phase_max = Phase_max(30:end-30);%Cut off edges to minimize edge effects
+Phase_max = Phase_max(30:end-30); %Cut off edges to minimize edge effects
 WrappedPhase = Phase_max';
-WrappedPhase = wrapToPi(WrappedPhase);
+% WrappedPhase = wrapToPi(WrappedPhase);
 TDPhase = unwrap(Phase_max)'+2*pi;
 % size(Phase_max)
 % TDPhase = wrapToPi(Phase_max_u)';

### 2014-08-29 Matlab/Phase_Detectors_Generate_Figure1.m
updated Figure 1 codes

@@ -45,7 +45,7 @@ YMin = 1.1*min(GWNSignal(:,SNRLoc));
 figure(1); clf
 
 subplot('Position',[l,b3,w,h])
-    plot(Time,TDSignal(30:end-30),'k-')
+    plot(Time,TDSignal,'k-')
         ylim([-1.3 1.3])
         set(gca,'XTickLabel','')
         box off
@@ -54,7 +54,7 @@ subplot('Position',[l,b3,w,h])
 
         
 subplot('Position',[l,b2,w,h])
-    plot(Time,GWNSignal(30:end-30,SNRLoc),'k-')
+    plot(Time,GWNSignal(:,SNRLoc),'k-')
         ylim([YMin YMax])
         set(gca,'XTickLabel','')
         box off
@@ -63,16 +63,17 @@ subplot('Position',[l,b2,w,h])
 
         
 subplot('Position',[l,b1,w,h])
-    plot(Time,TDPhaseUnwrap(30:end-30),'k--'); hold on
+    plot(Time,TDPhaseUnwrap,'k--'); hold on
     plot(Time,NoisyPhase_Hilb,'color',DGrey)
     plot(Time,NoisyPhase_Wave,'color',LGrey)
         legend('True','Hilbert','Wavelet','Location','NorthWest')
+        ylim([-5 180])
         box off
         text(-15,100,'Phase (rad)','FontName',FontN,'FontSize',FontSz,'HorizontalAlignment','Center','Rotation',90)
         text(60,-40,'Time (s)','FontName',FontN,'FontSize',FontSz,'HorizontalAlignment','Center','Rotation',0)
         text(-20,200,'C','FontName',FontN,'FontSize',FontSz+4,'FontWeight','Bold','HorizontalAlignment','Center','Rotation',0)
 %%
-print('-depsc2','/Users/nickmitrou/Documents/SFU/PhD/Projects/Phase_detectors/Results/Figure1.eps')
+print('-depsc2','/Users/nickmitrou/Documents/SFU/PhD/Projects/Phase_detectors/Results/Figure01.eps')
 
 
 

### 2014-08-29 Matlab/Phase_detectors_compare_run.m

@@ -23,8 +23,8 @@ f2 = CentralFreq+(0.5*CentralFreq);
 
 TDPhase_Hilb =  hilbert_interp(TDSignal,DT,Filt,f1,f2,Graphic);
 
-GWNPhase_Hilb = zeros([Length/DT+1-59,NoiseSteps]);
-GWNWrappedPhase_Hilb = zeros([Length/DT+1-59,NoiseSteps]);
+GWNPhase_Hilb = zeros([Length/DT+1,NoiseSteps]);
+GWNWrappedPhase_Hilb = zeros([Length/DT+1,NoiseSteps]);
 for k = 1:NoiseSteps
     [GWNPhase_Hilb(:,k), GWNWrappedPhase_Hilb(:,k)] = hilbert_interp(GWNSignal(:,k),DT,Filt, f1,f2,Graphic);
 end
@@ -32,8 +32,8 @@ end
 
 TDPhase_Wave =  wavelet_interp(TDSignal, DT,Filt, f1, f2, Graphic);
 
-GWNPhase_Wave = zeros([Length/DT+1-59,NoiseSteps]);
-GWNWrappedPhase_Wave = zeros([Length/DT+1-59,NoiseSteps]);
+GWNPhase_Wave = zeros([Length/DT+1,NoiseSteps]);
+GWNWrappedPhase_Wave = zeros([Length/DT+1,NoiseSteps]);
 for k = 1:NoiseSteps
     [GWNPhase_Wave(:,k), GWNWrappedPhase_Wave(:,k)] = wavelet_interp(GWNSignal(:,k), DT, Filt, f1, f2, Graphic);
 end
@@ -41,12 +41,12 @@ end
 % Determine agreement between each estimate and the true phase (Bland-Altman)
 GraphicBA = 0;
 % for noise free signals
-[Difference_Hilb1,MeanEst_Hilb1,MeanDiff_Hilb1,STDDiff_Hilb1] = BlandAltman(TDPhaseUnwrap(30:end-30),TDPhase_Hilb',GraphicBA);
-[Difference_Wave1,MeanEst_Wave1,MeanDiff_Wave1,STDDiff_Wave1] = BlandAltman(TDPhaseUnwrap(30:end-30),TDPhase_Wave,GraphicBA);
[…]

### 2014-08-29 Matlab/Phase_detectors_compare_trials.m

@@ -89,9 +89,9 @@ ylim([ymin ymax])
 text(((xmax-xmin)/2),-1.4,'Time (s)','HorizontalAlignment','center')
 text(0,-6,'Ampltidude','HorizontalAlignment','center','Rotation',90)
 %% Plot True, Hilbert and Wavelet Phase
-Time = Time(30:end-30);
+Time = Time;
 figure(2); clf;
-plot(Time,TDPhaseUnwrap(30:end-30),'k-',Time,unwrap(TDPhase_Hilb),'bo',Time,TDPhase_Wave,'ro')
+plot(Time,TDPhaseUnwrap,'k-',Time,unwrap(TDPhase_Hilb),'bo',Time,TDPhase_Wave,'ro')
 xlim([0 100])
 xlabel 'Time (s)'
 ylabel 'Phase (rad)'

### 2014-08-29 Matlab/BlandAltman.m
Dimension fool-proofing of Bland-Altman

@@ -3,10 +3,14 @@ function [Difference,MeanEst,MeanDiff,STDDiff] = BlandAltman(Sig1,Sig2,Graphic, 
 %%
 Size = size(Sig1);
 if Size(1)>Size(2)
-    EstPhases = [Sig1, Sig2];
-else
-    EstPhases = [Sig1; Sig2]';
+    Sig1 = Sig1';
 end
+Size = size(Sig2);
+if Size(1)>Size(2)
+    Sig2 = Sig2';
+end
+EstPhases = [Sig1; Sig2]';
+
 MeanEst = mean(EstPhases,2);
 
 Difference = Sig1 - Sig2;

### 2014-08-29 Matlab/LatexTableFromData.m
Created some code to create a Latex table from data

@@ -1,0 +1,25 @@
+function LatexTableFromData( OutputLocation, varargin )
+%%
+DummyVector = varargin{1};
+fileID = fopen(OutputLocation,'w');
+fprintf(fileID,'\\begin{tabular}{|');
+for N = 1:length(DummyVector)
+    fprintf(fileID,'c|'); 
+end
+fprintf(fileID,'}\n\\hline');
+%%
+FormatSpec = [];
+FormatSpec2 = '& %s';
+for N = 1:length(DummyVector)-1
+    FormatSpec = [FormatSpec,FormatSpec2];
+end
+FormatSpec = ['%s',FormatSpec,'\\\\ \\hline\n'];
+%%
+for N = 1:nargin
+    Vector = varargin{N};
+    fprintf(fileID,FormatSpec,Vector{:});
+end
+fprintf(fileID,'\\end{tabular}');
+fclose(fileID);
+end
+

### 2014-08-29 Matlab/TestForPositivePhase.m

@@ -1,0 +1,31 @@
+clear all; clc;
+%%
+CentralFreq = 0.4;
+STDFreq = CentralFreq*0.1;
+Order = 50;
+Length = 120;
+DT = 0.1;
+Graphic = 0;
+
+SNRMin = -10;
+SNRMax = -10;
+NoiseSteps = SNRMax-SNRMin+1;
+NoiseVec = linspace(SNRMin,SNRMax,NoiseSteps);
+
+
+f1 = CentralFreq-(0.5*CentralFreq);
+f2 = CentralFreq+(0.5*CentralFreq);
+Filt=0;
+
+Differences = [];
+%%
+for N = 1:50
+    N
+    [TDSignal, TDPhase , TDPhaseUnwrap, Time, ~] = Time_varying_sinewave(CentralFreq, STDFreq, Order, Length, DT, Graphic);
+    NoisySignal = awgn(TDSignal,NoiseVec,'measured');
+    [WTDPhase, WWrappedPhase] =  wavelet_interp(TDSignal, DT, Filt,f1, f2, Graphic);
+    Difference =TDPhase-WWrappedPhase;
+    Differences = [Differences,mean(Difference(abs(Difference)<pi))];
+end
+mean(Differences)
+figure(69); clf; plot(Difference(abs(Difference)<pi))

### 2014-08-29 Matlab/wavelet_interp.m

@@ -39,7 +39,6 @@ for k = 1:Size
     [~,TempPeriod] = max(Power(:,k));
     Phase_max(k) = angle(WN(TempPeriod,k));
 end
-Phase_max = Phase_max(30:end-30); %Cut off edges to minimize edge effects
 WrappedPhase = Phase_max';
 % WrappedPhase = wrapToPi(WrappedPhase);
 TDPhase = unwrap(Phase_max)'+2*pi;

### 2014-08-29 Matlab/BlandAltman.m
updated to cut edges

@@ -1,5 +1,5 @@
 
-function [Difference,MeanEst,MeanDiff,STDDiff] = BlandAltman(Sig1,Sig2,Graphic, FigNo)
+function [Difference,MeanEst,MeanDiff,STDDiff] = BlandAltman(Sig1,Sig2,Graphic,FigNo,f1)
 %%
 Size = size(Sig1);
 if Size(1)>Size(2)
@@ -7,6 +7,7 @@ if Size(1)>Size(2)
 else
     EstPhases = [Sig1; Sig2]';
 end
+
 MeanEst = mean(EstPhases,2);
 
 Difference = Sig1 - Sig2;

### 2014-08-29 Matlab/Phase_detectors_compare_run.m

@@ -21,33 +21,40 @@ f1 = CentralFreq-(0.5*CentralFreq);
 f2 = CentralFreq+(0.5*CentralFreq);
 
 
-TDPhase_Hilb =  hilbert_interp(TDSignal,DT,Filt,f1,f2,Graphic);
+[TDPhase_Hilb, ~, ~] =  hilbert_interp(TDSignal,DT,Filt,f1,f2,Graphic);
 
 GWNPhase_Hilb = zeros([Length/DT+1,NoiseSteps]);
 GWNWrappedPhase_Hilb = zeros([Length/DT+1,NoiseSteps]);
 for k = 1:NoiseSteps
-    [GWNPhase_Hilb(:,k), GWNWrappedPhase_Hilb(:,k)] = hilbert_interp(GWNSignal(:,k),DT,Filt, f1,f2,Graphic);
+    [GWNPhase_Hilb(:,k), ~, GWNWrappedPhase_Hilb(:,k)] = hilbert_interp(GWNSignal(:,k),DT,Filt, f1,f2,Graphic);
 end
 % Estimate phase with wavelet transform
 
-TDPhase_Wave =  wavelet_interp(TDSignal, DT,Filt, f1, f2, Graphic);
+[TDPhase_Wave, ~, ~] =  wavelet_interp(TDSignal, DT,Filt, f1, f2, Graphic);
 
 GWNPhase_Wave = zeros([Length/DT+1,NoiseSteps]);
 GWNWrappedPhase_Wave = zeros([Length/DT+1,NoiseSteps]);
 for k = 1:NoiseSteps
-    [GWNPhase_Wave(:,k), GWNWrappedPhase_Wave(:,k)] = wavelet_interp(GWNSignal(:,k), DT, Filt, f1, f2, Graphic);
+    [GWNPhase_Wave(:,k), ~, GWNWrappedPhase_Wave(:,k)] = wavelet_interp(GWNSignal(:,k), DT, Filt, f1, f2, Graphic);
 end
 
 % Determine agreement between each estimate and the true phase (Bland-Altman)
 GraphicBA = 0;
 % for noise free signals
-[Difference_Hilb1,MeanEst_Hilb1,MeanDiff_Hilb1,STDDiff_Hilb1] = BlandAltman(TDPhaseUnwrap,TDPhase_Hilb',GraphicBA);
[…]

### 2014-08-29 Matlab/Phase_detectors_compare_trials.m

@@ -33,18 +33,22 @@ tic
 CentralFreq = 0.2;
 STDFreq = CentralFreq*0.1;
 Order = 12;
-Length = 120;
+Length = 300;
 DT = 0.1;
-Graphic = 0;
+Graphic = 1;
 
-SNRMin = -100;
-SNRMax = 4;
-NoiseSteps = 50;
+SNRMin = -10;
+SNRMax = 0;
+NoiseSteps = SNRMax-SNRMin+1;
 NoiseVec = linspace(SNRMin,SNRMax,NoiseSteps);
 
 
-Trials = 4;
+Trials = 1;
 %%
+    f1 = CentralFreq-(0.5*CentralFreq);
+    
+    CutS = ceil(3/f1/DT);
+    
 Difference_Hilb = [];
 MeanEst_Hilb = [];
 Difference_Wave = [];
@@ -53,7 +57,7 @@ MeanDiff_Hilb = zeros([Trials,NoiseSteps]);
 STDDiff_Hilb = zeros([Trials,NoiseSteps]);
 MeanDiff_Wave = zeros([Trials,NoiseSteps]);
 STDDiff_Wave = zeros([Trials,NoiseSteps]);
-Filt = 1;
+Filt = 0;
 for k = 1:Trials
     
     [Time,TDSignal,TDPhaseUnwrap,TDPhase_Hilb,TDPhase_Wave,Difference_Hilb1,...
@@ -67,7 +71,7 @@ end
 
 toc
 %
-Graphic=1;
+% Graphic=0;
 if Graphic == 1
 %% Plot TDSignal
 
@@ -126,7 +130,7 @@ legend('Hilbert','Wavelet')
 figure(4);clf;
 length(MeanEst_Hilb(:,1))
 length(MeanDiff_Hilb(:,1))
-plot(Time,Difference_Hilb(:,1),'k*',Time,Difference_Wave(:,1),'r*')
+plot(Time(CutS:end-CutS),Difference_Hilb(:,1),'k*',Time(CutS:end-CutS),Difference_Wave(:,1),'r*')
 %ylim([-1.5 1.5])
 title 'Bland-Altman plot for smallest SNR'
 xlabel 'Mean Estimated phase'

### 2014-08-29 Matlab/hilbert_interp.m

@@ -1,4 +1,4 @@
-function [TDPhase, WrappedPhase] =  hilbert_interp(Signal_f,Dt,Filt, f1,f2,Graphic)
+function [TDPhase, TDPhaseCut, WrappedPhase] =  hilbert_interp(Signal_f,DT,Filt, f1,f2,Graphic)
 %% Hilbert Interp %%
 % function purpose is to use the hilbert transform of a signal and estimate
 % the instantaneous phase and frequency of the signal
@@ -11,7 +11,7 @@ function [TDPhase, WrappedPhase] =  hilbert_interp(Signal_f,Dt,Filt, f1,f2,Graph
 %%%%%%%%%% Outputs %%%%%%%%%%
 % TDPhase - unwrapped instantaneous phase with phase slips interpolated
 
-Fs = 1/Dt;  % Sampling Frequency
+Fs = 1/DT;  % Sampling Frequency
 %FOR MYO
 N   = 6;    % Order
 % Construct an FDESIGN object and call its BUTTER method.
@@ -25,19 +25,23 @@ end
 xh = hilbert(Signal_f);
 phh = angle(xh);
 WrappedPhase = phh;
-WrappedPhase = WrappedPhase(30:end-30);%Cut off edges to minimize edge effect
-TDPhase = unwrap(phh(30:end-30))+2*pi;
+WrappedPhase = WrappedPhase;%Cut off edges to minimize edge effect
+TDPhase = unwrap(phh);
+
+CutS = ceil(3/f1*DT);
+
+TDPhaseCut = TDPhase(CutS:end-CutS);
 
     w = diff(TDPhase).*(2*2/pi);
     wi = w;
 %% find data points where inst. frequency is outside filter pass band, and interpolate across those points
- t = Dt:Dt:length(Signal_f)*Dt;
+ t = DT:DT:length(Signal_f)*DT;
  k1=find(wi<0);
  kk1=[k1;k1+1;k1-1];
  kk1(kk1<=0)=[];
  kk1(kk1>length(wi))=[];
  ti=t(2:end);
- ti = ti(30:end-30);
+ ti = ti;
  tt=ti;
  tt(kk1)=[];
 % wi(kk1)=[];
@@ -49,7 +53,7 @@ TDPhase = unwrap(phh(30:end-30))+2*pi;
 phh4=WrappedPhase(2:end);
 phh4(kk1)=[];
 phh4=interp1(tt,phh4,ti,'linear','extrap')';
[…]

### 2014-08-29 Matlab/wavelet_interp.m

@@ -1,4 +1,4 @@
-function [TDPhase, WrappedPhase] =  wavelet_interp(TDSignal, DT, Filt,f1, f2, Graphic)
+function [TDPhase, TDPhaseCut, WrappedPhase] =  wavelet_interp(TDSignal, DT, Filt,f1, f2, Graphic)
 %%
 Time = 0:length(TDSignal)-1;
 Time=Time.*DT;
@@ -39,10 +39,15 @@ for k = 1:Size
     [~,TempPeriod] = max(Power(:,k));
     Phase_max(k) = angle(WN(TempPeriod,k));
 end
-Phase_max = Phase_max(30:end-30); %Cut off edges to minimize edge effects
+Phase_max = Phase_max; %Cut off edges to minimize edge effects
 WrappedPhase = Phase_max';
 % WrappedPhase = wrapToPi(WrappedPhase);
-TDPhase = unwrap(Phase_max)'+2*pi;
+TDPhase = unwrap(Phase_max)';
+
+CutS = ceil(3/f1*DT);
+
+TDPhaseCut = TDPhase(CutS:end-CutS);
+
 % size(Phase_max)
 % TDPhase = wrapToPi(Phase_max_u)';
 if Graphic

### 2014-08-29 Matlab/wavelet_interp.m
replaced wavelet_interp

@@ -1,0 +1,52 @@
+function [TDPhase, WrappedPhase] =  wavelet_interp(TDSignal, DT, Filt,f1, f2, Graphic)
+%%
+Time = 0:length(TDSignal)-1;
+Time=Time.*DT;
+dj=0.04; %wavelet interval
+J1=127; %total # of scales
+pad=1; %zero-pad signals
+s0=0.5; %set initial scale
+mother='Morlet'; %wavelet shape
+param=6; %initial wavelet order
+
+Fs = 1/DT;  % Sampling Frequency
+%FOR MYO
+N   = 6;    % Order
+% Construct an FDESIGN object and call its BUTTER method.
+h  = fdesign.bandpass('N,F3dB1,F3dB2', N, f1, f2, Fs);
+Hd = design(h, 'butter');
+[b,a]=sos2tf(Hd.sosMatrix,Hd.ScaleValues);
+
+if Filt
+    TDSignal = filtfilt(b,a,TDSignal); %bandpass filter the input signal
+end
+
+
+%computes the wavelets
+[WN,Period,~] = wavelet(TDSignal,DT,pad,dj,s0,J1,mother,param);
+Power = abs(WN).^2;
+%Freqs=1./(1.033.*Scale);
+if Graphic
+    figure(1);clf;
+    mesh(Time, Period, Power) 
+    view(90,45);
+    colormap(hot)
+end
+%
+Size = size(Power,2);
+Phase_max = zeros(Size,1);
+for k = 1:Size
+    [~,TempPeriod] = max(Power(:,k));
+    Phase_max(k) = angle(WN(TempPeriod,k));
+end
+WrappedPhase = Phase_max';
+% WrappedPhase = wrapToPi(WrappedPhase);
+TDPhase = unwrap(Phase_max)'+2*pi;
+% size(Phase_max)
+% TDPhase = wrapToPi(Phase_max_u)';
+if Graphic
+   figure(2); clf
+   plot(TDPhase);
+end
+%wi = (diff(Phase_max_u).*2*2/pi)';
+end

### 2014-08-29 Matlab/Phase_Detectors_Generate_Figure2.m
nicer figure 2

@@ -1,0 +1,21 @@
+%%%%%%%%%%%% Figure 2 %%%%%%%%%%%%
+
+Phase_detectors_compare_trials
+%%
+
+for k = 1:floor(length(NoiseVec))
+    PhaseDiff_HilbMean(k) = mean(MeanDiff_Hilb(:,k));
+    PhaseDiff_WaveMean(k) = mean(MeanDiff_Wave(:,k));
+
+    PhaseDiff_HilbSTD(k) = std(MeanDiff_Hilb(:,k));
+    PhaseDiff_WaveSTD(k) = std(MeanDiff_Wave(:,k));
+end
+
+%%
+
+figure(2); clf
+errorbar(NoiseVec,PhaseDiff_HilbMean,PhaseDiff_HilbSTD,'k-'); hold on
+errorbar(NoiseVec,PhaseDiff_WaveMean,PhaseDiff_WaveSTD,'r-')
+    xlim([-81 61])
+    ylim([-0.2 0.2])
+    

### 2014-08-29 Matlab/Phase_Detectors_Generate_Figure2.m
Figure updated

@@ -19,3 +19,9 @@ errorbar(NoiseVec,PhaseDiff_WaveMean,PhaseDiff_WaveSTD,'r-')
     xlim([-81 61])
     ylim([-0.2 0.2])
     
+%% Export table data
+Row1 = {num2str(NoiseVec(51)),[num2str(PhaseDiff_HilbMean(51)) ' $\pm$ ' num2str(PhaseDiff_HilbSTD(51))],[num2str(PhaseDiff_WaveMean(51)) ' $\pm$ ' num2str(PhaseDiff_WaveSTD(51))]};
+
+OutputLocation = '/Users/nickmitrou/Documents/SFU/PhD/Projects/Phase_detectors/Manuscript/TestTable.txt';
+
+LatexTableFromData( OutputLocation, Row1 );

### 2014-09-03 Matlab/BlandAltman.m
Added BlandAltman

@@ -1,0 +1,30 @@
+
+function [Difference,MeanEst,MeanDiff,STDDiff] = BlandAltman(Sig1,Sig2,Graphic, FigNo)
+%%
+Size = size(Sig1);
+if Size(1)>Size(2)
+    Sig1 = Sig1';
+end
+Size = size(Sig2);
+if Size(1)>Size(2)
+    Sig2 = Sig2';
+end
+EstPhases = [Sig1; Sig2]';
+
+MeanEst = mean(EstPhases,2);
+
+Difference = Sig1 - Sig2;
+
+MeanDiff = mean(Difference);
+STDDiff = std(Difference);
+
+if Graphic == 1
+    figure(FigNo); clf;
+    plot(MeanEst,Difference,'ko'); hold on;
+    plot([min(MeanEst) max(MeanEst)],[MeanDiff MeanDiff],'r-');
+    plot([min(MeanEst) max(MeanEst)],[MeanDiff+1.96*STDDiff MeanDiff+1.96*STDDiff],'r--');
+    plot([min(MeanEst) max(MeanEst)],[MeanDiff-1.96*STDDiff MeanDiff-1.96*STDDiff],'r--');
+    xlabel 'Mean'
+    ylabel 'Difference'
+end
+end
